---
title: "Intrinsic continuity is equivalent to the Kirchhoff condition for degree-two vertices"
date: "Last modified: `r format(Sys.time(), '%d-%m-%Y.')`"
output:
  html_document:
    mathjax: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
    highlight: pygments
    theme: flatly
    code_folding: hide # class.source = "fold-hide" to hide code and add a button to show it
    df_print: paged
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
    fig_caption: true
    code_download: true
    css: visual.css
always_allow_html: true
bibliography: 
  - references.bib
  - grateful-refs.bib
header-includes:
  - \newcommand{\ar}{\mathbb{R}}
  - \newcommand{\llav}[1]{\left\{#1\right\}}
  - \newcommand{\pare}[1]{\left(#1\right)}
  - \newcommand{\Ncal}{\mathcal{N}}
  - \newcommand{\Vcal}{\mathcal{V}}
  - \newcommand{\Ecal}{\mathcal{E}}
  - \newcommand{\Wcal}{\mathcal{W}}
  - \newcommand{\almosteverywhere}{\mathrm{a.e.}\;}
---

Go back to the [Contents](about.html) page.

<div style="color: #2c3e50; text-align: right;">
********  
<strong>Press Show to reveal the code chunks.</strong>  

********
</div>


```{r}
# Create a clipboard button on the rendered HTML page
source(here::here("clipboard.R")); clipboard
# Set seed for reproducibility
set.seed(1982) 
# Set global options for all code chunks
knitr::opts_chunk$set(
  # Disable messages printed by R code chunks
  message = FALSE,    
  # Disable warnings printed by R code chunks
  warning = FALSE,    
  # Show R code within code chunks in output
  echo = TRUE,        
  # Include both R code and its results in output
  include = TRUE,     
  # Evaluate R code chunks
  eval = FALSE,       
  # Enable caching of R code chunks for faster rendering
  cache = FALSE,      
  # Align figures in the center of the output
  fig.align = "center",
  # Enable retina display for high-resolution figures
  retina = 2,
  # Show errors in the output instead of stopping rendering
  error = TRUE,
  # Do not collapse code and output into a single block
  collapse = FALSE
)
# Start the figure counter
fig_count <- 0
# Define the captioner function
captioner <- function(caption) {
  fig_count <<- fig_count + 1
  paste0("Figure ", fig_count, ": ", caption)
}

```

```{r, eval = TRUE}
library(MetricGraph)
library(ggplot2)
library(reshape2)
library(dplyr)
library(viridis)
library(plotly)
library(patchwork)
library(slackr)
source("keys.R")
slackr_setup(token = token) # token comes from keys.R
```


```{r}
capture.output(
  knitr::purl(here::here("functionality1.Rmd"), output = here::here("functionality1.R")),
  file = here::here("old/purl_log.txt")
)
source(here::here("functionality1.R"))
```



```{r}
x_eye <- 5#8
y_eye <- -1#-2
z_eye <- 2#3
```

Let $\Gamma = (\mathcal{V}, \mathcal{E})$ be a metric graph with vertex set $\mathcal{V} = \{v_1, v, v_2\}$ and edge set $\mathcal{E} = \{e_1, e_2\}$. Assume that the edges $e_1$ and $e_2$ meet at the vertex $v$, so that $v$ is their common endpoint. For later reference, we recall the Kirchhoff vertex conditions
\begin{equation}
\label{eq:kirchhoff_cond}
\tag{1}
   \mathcal{K}(\Gamma) =  \left\{f\in C(\Gamma)\;\middle|\; \forall v\in \mathcal{V}:\; \sum_{e\in\mathcal{E}_v}\partial_e f(v)=0 \right\},
\end{equation}
where $\mathcal{E}_v$ denotes the set of edges incident to $v$, and
\begin{equation}
\label{eq:dir_der}
\tag{2}
        \partial_ef(v) = 
        \begin{cases}
            f'_e(0), \quad &\text{if }v=0,\\
            -f'_e(\ell_e), \quad &\text{if }v=\ell_e.
        \end{cases}
\end{equation}

# Compatible orientation

```{r}
apply_edge_functions_fast <- function(graph, f_list) {
  
  if (length(f_list) != graph$nE) {
    stop(sprintf(
      "Number of functions (%d) must equal number of edges (%d).",
      length(f_list), graph$nE
    ))
  }
  VtE <- graph$mesh$VtE
  edge_lengths <- graph$edge_lengths
  
  edge   <- VtE[,1]
  s_norm <- VtE[,2]
  s_true <- s_norm * edge_lengths[edge]

  out <- sapply(seq_len(nrow(VtE)), function(i) f_list[[edge[i]]](s_true[i]))
  return(out)
}
```


We first assume that the edges are compatibly oriented, namely $e_1 = [0,\ell_1]$ and $e_2=[0,\ell_2]$, with the vertex $v$ corresponding to $\ell_1$ on $e_1$ and $0$ on $e_2$. With this parametrization, we can glue the two edges into a single interval $[e_1,e_2]\simeq [0,\ell_1+\ell_2]$ and view a function $f = \{f_{e_1},f_{e_2}\}\in C(\Gamma)$ as a function $\hat{f}\in C([0,\ell_1+\ell_2])$ so that $f_{e_1}(\ell_1) = \hat{f}(v) = f_{e_2}(0)$. Consider the function $f = \{f_{e_1},f_{e_2}\}$ given by
\begin{equation*}
    \begin{cases}
        f_{e_1}(t) = t^4,& t\in[0,\ell_1],\\
        f_{e_2}(t) = (t+\ell_1)^4,& t\in[0,\ell_2].
    \end{cases}
\end{equation*}
Its edgewise derivatives are given by
\begin{equation*}
    \begin{cases}
        f'_{e_1}(t) = 4t^3,& t\in[0,\ell_1],\\
        f'_{e_2}(t) = 4(t+\ell_1)^3,& t\in[0,\ell_2].
    \end{cases}
\end{equation*}
Under the above identification, $f$ corresponds to the function
\begin{align*}
    \hat{f}(t) = t^4,\quad t\in[0,\ell_1 + \ell_2],
\end{align*}
whose derivative is
\begin{align*}
    \hat{f}(t) = 4t^3,\quad t\in[0,\ell_1 + \ell_2].
\end{align*}
In particular, $\hat{f} \in C^1([0,\ell_1+\ell_2])$, and therefore $f$ has a continuous first derivative across the vertex $v$. See Figure 2. Moreover, the edgewise derivatives must agree at $v$, that is, we must have $f'_{e_1}(\ell_1) = \hat{f}'(v) = f'_{e_2}(0)$, which is the case since
\begin{align*}
    f'_{e_1}(\ell_1) = 4\ell_1^3\quad\text{ and }\quad  \hat{f}'(v) = \hat{f}'(\ell_1)=4\ell_1^3\quad \text{ and }\quad f'_{e_2}(0)  = 4\ell_1^3.
\end{align*}
By using \eqref{eq:dir_der}, we get that 
\begin{align*}
        \partial_{e_1}f(v) = -f'_{e_1}(\ell_1)=-4\ell_1^3\quad\text{ and }\quad \partial_{e_2}f(v) = f'_{e_2}(0)=4\ell_1^3,
\end{align*}
and therefore,
\begin{equation}
\sum_{e \in \mathcal{E}_v} \partial_e f(v) =\partial_{e_1}f(v) + \partial_{e_2}f(v) = -f'_{e_1}(\ell_1) + f'_{e_2}(0) = -4\ell_1^3 + 4\ell_1^3 = 0,
\end{equation}
which means that $f$ satisfies the Kirchhoff vertex conditions \eqref{eq:kirchhoff_cond} at vertex $v$. This is an instance of the fact that $f$ satisfies the Kirchhoff vertex conditions \eqref{eq:kirchhoff_cond} at all vertices $v$ with $\deg(v) =2$ if and only if $f'$ is continuous at at all vertices $v$ with $\deg(v) =2$.


```{r}
h = 0.01
ell1 <- 1
ell2 <- 0.4
e1 <- rbind(c(-ell1,0), # (x,y) = underline(e_1) 
            c(0,0))  # (x,y) = overline(e_1) 
e2 <- rbind(c(0,0),
            c(ell2,0))

e1_ini_x <- -ell1; e1_ini_y <- 0; e1_ini_z <- 0
e1_fin_x <- 0; e1_fin_y <- 0; e1_fin_z <- 0

# Midpoint
xm1 <- (e1_fin_x + e1_ini_x)/2
ym1 <- (e1_fin_y + e1_ini_y)/2
zm1 <- (e1_fin_z + e1_ini_z)/2

# Direction vector
dx1 <- e1_fin_x - e1_ini_x
dy1 <- e1_fin_y - e1_ini_y
dz1 <- e1_fin_z - e1_ini_z

e2_ini_x <- 0; e2_ini_y <- 0; e2_ini_z <- 0
e2_fin_x <- ell2; e2_fin_y <- 0; e2_fin_z <- 0

# Midpoint
xm2 <- (e2_fin_x + e2_ini_x)/2
ym2 <- (e2_fin_y + e2_ini_y)/2
zm2 <- (e2_fin_z + e2_ini_z)/2

# Direction vector
dx2 <- e2_fin_x - e2_ini_x
dy2 <- e2_fin_y - e2_ini_y
dz2 <- e2_fin_z - e2_ini_z


graph <- metric_graph$new(edges = list(e1 = e1, e2 = e2))
graph$build_mesh(h = h)
```


```{r}
fe1 <- function(t) t^4
fe2 <- function(t) (t + ell1)^4

dfe1 <- function(t) 4*t^3
dfe2 <- function(t) 4*(t + ell1)^3

ddfe1 <- function(t) 12*t^2
ddfe2 <- function(t) 12*(t + ell1)^2

dddfe1 <- function(t) 24*t
dddfe2 <- function(t) 24*(t + ell1)

f_list <- list(fe1, fe2)
df_list <- list(dfe1, dfe2)
ddf_list <- list(ddfe1, ddfe2)
dddf_list <- list(dddfe1, dddfe2)

f_list_aux <- f_list

f <- apply_edge_functions_fast(graph, f_list)
df <- apply_edge_functions_fast(graph, df_list)
ddf <- apply_edge_functions_fast(graph, ddf_list)
dddf <- apply_edge_functions_fast(graph, dddf_list)
```



```{r}
sizeref <- 0.1
pf <- graph$plot_function(X = f, vertex_size = gsw, edge_width = gsw, line_width = gsw, type = "plotly") |> 
  add_trace(
  type = "cone",
  x = ym1,
  y = xm1,
  z = zm1,
  u = dy1,
  v = dx1,
  w = dz1,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("green", "green")),
  cmin = 0,
  cmax = 1
) |>
  add_trace(
  type = "cone",
  x = ym2,
  y = xm2,
  z = zm2,
  u = dy2,
  v = dx2,
  w = dz2,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("green", "green")),
  cmin = 0,
  cmax = 1
) |>
  config(mathjax = 'cdn') |>
  plotly::layout(title = list(text = TeX("f"), y = 0.8),
                 font = list(family = "Palatino"),
                 scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
                   aspectratio = list(x = 2, 
                                 y = 2, 
                                 z = 2),
                   camera = list(eye = list(x = x_eye, 
                                       y = y_eye, 
                                       z = z_eye),
                            center = list(x = 0, 
                                          y = 0, 
                                          z = 0)),
                   annotations = list(
                     
             list(
               x = e1_ini_y, y = e1_ini_x, z = e1_ini_z,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = 0, y = 0, z = 0,
               text = TeX("v"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = e2_fin_y, y = e2_fin_x, z = e2_fin_z,
               text = TeX("v_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym1, y = xm1, z = zm1,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym2, y = xm2, z = zm2,
               text = TeX("e_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"))
                 ))

pdf <- graph$plot_function(X = df, vertex_size = gsw, edge_width = gsw, line_width = gsw, type = "plotly") |> 
  add_trace(
  type = "cone",
  x = ym1,
  y = xm1,
  z = zm1,
  u = dy1,
  v = dx1,
  w = dz1,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("green", "green")),
  cmin = 0,
  cmax = 1
) |>
  add_trace(
  type = "cone",
  x = ym2,
  y = xm2,
  z = zm2,
  u = dy2,
  v = dx2,
  w = dz2,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("green", "green")),
  cmin = 0,
  cmax = 1
) |>
  config(mathjax = 'cdn') |>
  plotly::layout(title = list(text = TeX("f'"), y = 0.8),
                 font = list(family = "Palatino"),
                 scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
                   aspectratio = list(x = 2, 
                                 y = 2, 
                                 z = 2),
                   camera = list(eye = list(x = x_eye, 
                                       y = y_eye, 
                                       z = z_eye),
                            center = list(x = 0, 
                                          y = 0, 
                                          z = 0)),
                   annotations = list(
                     
             list(
               x = e1_ini_y, y = e1_ini_x, z = e1_ini_z,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = 0, y = 0, z = 0,
               text = TeX("v"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = e2_fin_y, y = e2_fin_x, z = e2_fin_z,
               text = TeX("v_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym1, y = xm1, z = zm1,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym2, y = xm2, z = zm2,
               text = TeX("e_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"))
                 ))

pddf <- graph$plot_function(X = ddf, vertex_size = gsw, edge_width = gsw, line_width = gsw, type = "plotly") |>
  add_trace(
  type = "cone",
  x = ym1,
  y = xm1,
  z = zm1,
  u = dy1,
  v = dx1,
  w = dz1,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("green", "green")),
  cmin = 0,
  cmax = 1
) |>
  add_trace(
  type = "cone",
  x = ym2,
  y = xm2,
  z = zm2,
  u = dy2,
  v = dx2,
  w = dz2,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("green", "green")),
  cmin = 0,
  cmax = 1
) |>
  config(mathjax = 'cdn') |>
  plotly::layout(title = list(text = TeX("f''"), y = 0.8), 
                 font = list(family = "Palatino"),
                 scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
                   aspectratio = list(x = 2, 
                                 y = 2, 
                                 z = 2),
                   camera = list(eye = list(x = x_eye, 
                                       y = y_eye, 
                                       z = z_eye),
                            center = list(x = 0, 
                                          y = 0, 
                                          z = 0)),
                   annotations = list(
                     
             list(
               x = e1_ini_y, y = e1_ini_x, z = e1_ini_z,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = 0, y = 0, z = 0,
               text = TeX("v"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = e2_fin_y, y = e2_fin_x, z = e2_fin_z,
               text = TeX("v_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym1, y = xm1, z = zm1,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym2, y = xm2, z = zm2,
               text = TeX("e_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"))
                 ))

pdddf <- graph$plot_function(X = dddf, vertex_size = gsw, edge_width = gsw, line_width = gsw, type = "plotly") |> 
  add_trace(
  type = "cone",
  x = ym1,
  y = xm1,
  z = zm1,
  u = dy1,
  v = dx1,
  w = dz1,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("green", "green")),
  cmin = 0,
  cmax = 1
) |>
  add_trace(
  type = "cone",
  x = ym2,
  y = xm2,
  z = zm2,
  u = dy2,
  v = dx2,
  w = dz2,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("green", "green")),
  cmin = 0,
  cmax = 1
) |>
  config(mathjax = 'cdn') |>
  plotly::layout(title = list(text = TeX("f'''"), y = 0.8),
                 font = list(family = "Palatino"),
                 scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
                   aspectratio = list(x = 2, 
                                 y = 2, 
                                 z = 2),
                   camera = list(eye = list(x = x_eye, 
                                       y = y_eye, 
                                       z = z_eye),
                            center = list(x = 0, 
                                          y = 0, 
                                          z = 0)),
                   annotations = list(
                     
             list(
               x = e1_ini_y, y = e1_ini_x, z = e1_ini_z,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = 0, y = 0, z = 0,
               text = TeX("v"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = e2_fin_y, y = e2_fin_x, z = e2_fin_z,
               text = TeX("v_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym1, y = xm1, z = zm1,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym2, y = xm2, z = zm2,
               text = TeX("e_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"))
                 ))

save(pf, file = here::here("data_files/pf.Rdata"))
save(pdf, file = here::here("data_files/pdf.Rdata"))
save(pddf, file = here::here("data_files/pddf.Rdata"))
save(pdddf, file = here::here("data_files/pdddf.Rdata"))
```


:::: {style="display: grid; grid-template-columns: 485px 485px 485px 485px; grid-column-gap: 0px;"}


::: {}

```{r, eval = TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Function $f = \\{f_e\\}_{e\\in\\mathcal{E}}$ given by $f_{e_1}(t) = t^4$ and $f_{e_2}(t) = (t+\\ell_1)^4$.")}
load(here::here("data_files/pf.Rdata"))
pf
```

:::


::: {}

```{r, eval = TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Function $f' = \\{f'_e\\}_{e\\in\\mathcal{E}}$ given by $f'_{e_1}(t) = 4t^3$ and $f'_{e_2}(t) = 4(t+\\ell_1)^3$.")}
load(here::here("data_files/pdf.Rdata"))
pdf
```

:::


::: {}

```{r, eval = TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Function $f'' = \\{f''_e\\}_{e\\in\\mathcal{E}}$ given by $f''_{e_1}(t) = 12t^2$ and $f''_{e_2}(t) = 12(t+\\ell_1)^2$.")}
load(here::here("data_files/pddf.Rdata"))
pddf
```

:::


::: {}

```{r, eval = TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Function $f''' = \\{f'''_e\\}_{e\\in\\mathcal{E}}$ given by $f'''_{e_1}(t) = 24t$ and $f'''_{e_2}(t) = 24(t+\\ell_1)$.")}
load(here::here("data_files/pdddf.Rdata"))
pdddf
```


:::

::::


# Incompatible orientation



```{r}
my_apply_edge_functions <- function(graph, f_list, ell1, ell2, h){
  l1_mesh <- seq(0, ell1, by = h)
  l2_mesh <- seq(0, ell2, by = h)
  f1 <- f_list[[1]](l1_mesh)
  f2 <- f_list[[2]](l2_mesh)
  l1_mesh_norm <- l1_mesh/ell1
  l2_mesh_norm <- l2_mesh/ell2
  PtE1 <- cbind(rep(1, length(l1_mesh)), l1_mesh_norm)
  PtE2 <- cbind(rep(2, length(l2_mesh)), l2_mesh_norm)
  XY1 <- graph$coordinates(PtE1)
  XY2 <- graph$coordinates(PtE2)
  DF1 <- data.frame(x = XY1[,1], y = XY1[,2], z = f1)
  DF2 <- data.frame(x = XY2[,1], y = XY2[,2], z = f2)
  DF <- rbind(DF1, rep(NA, 3), DF2)
  return(list(DF = DF))
}
```

Now study the case where the edges are not compatible oriented. For that, we flip edge $e_2$, that is, $e_1 = [0,\ell_1]$ and $e_2=[0,\ell_2]$ with $v$ corresponding to $\ell_1$ on $e_1$ and $\ell_2$ on $e_2$. Consider the function $g = \{g_{e_1},g_{e_2}\}$ given by
\begin{equation*}
    \begin{cases}
        g_{e_1}(\tau) = \tau^4,& \tau\in[0,\ell_1],\\
        g_{e_2}(\tau) = (\tau-(\ell_1+\ell_2))^4,& \tau\in[0,\ell_2].
    \end{cases}
\end{equation*}
Its edgewise derivatives are given by
\begin{equation*}
    \begin{cases}
        g'_{e_1}(\tau) = 4\tau^3,& \tau\in[0,\ell_1],\\
        g'_{e_2}(\tau) = 4(\tau-(\ell_1+\ell_2))^3,& \tau\in[0,\ell_2].
    \end{cases}
\end{equation*}
The coordinates derivatives at $v$ are given by
\begin{equation}
g'_{e_1}(\ell_1)=4\ell_1^3\quad\text{ and }\quad g'_{e_2}(\ell_2)=-4\ell_1^3.
\end{equation}
Let us check the Kirchhoff vertex conditions \eqref{eq:kirchhoff_cond} at vertex $v$. By using \eqref{eq:dir_der}, we get that 
\begin{align*}
        \partial_{e_1}g(v) = -g'_{e_1}(\ell_1)=-4\ell_1^3\quad\text{ and }\quad \partial_{e_2}g(v) = -g'_{e_2}(\ell_2)=4\ell_1^3,
\end{align*}
and therefore,
\begin{equation}
\label{eq:invariant_c}
\tag{3}
\sum_{e \in \mathcal{E}_v} \partial_e g(v) =\partial_{e_1}g(v) + \partial_{e_2}g(v) = -g'_{e_1}(\ell_1) -g'_{e_2}(\ell_2) = -4\ell_1^3 + 4\ell_1^3 = 0,
\end{equation}
which shows that $g$ satisfies the Kirchhoff vertex conditions \eqref{eq:kirchhoff_cond} at vertex $v$. At first glance, the edgewise derivative, $g' = \{g'_{e_1},g'_{e_2}\}$ appears discontinuous at $v$, which might seem contradictory. See Figure 6.

To clarify, observe that $f = g$ as functions on the graph. Indeed, by reparametrizing edge $e_1$ by $\tau=t$ and edge $e_2$ by $\tau = \ell_2-t$, we obtain $f_{e_1}=g_{e_1}$  and $f_{e_2}=g_{e_2}$. More precisely,
\begin{align}
\label{eq:eq_of_f_g}
\tag{4}
     g_{e_1}(\tau) = g_{e_1}(t) = t^4 = f_{e_1}(t)\quad\text{ and }\quad   g_{e_2}(\tau) = g_{e_2}(\ell_2-t) = (\ell_2-t-(\ell_1+\ell_2))^4 = (t+\ell_1)^4= f_{e_2}(t),
\end{align}
Thus $f$ and $g$ coincide on each edge after reparametrization, and define the same function on the graph. The apparent discontinuity of $g'$ arises solely from the reversed coordinate on $e_2$. The function itself has not changed, only its coordinate representation.

From \eqref{eq:eq_of_f_g}, by the chain rule, the first derivative transforms as
\begin{equation}
\label{eq:der_inv}
\tag{5}
g'_{e_2}(\tau) = \dfrac{d}{d\tau} (g_{e_2}(\tau)) = \dfrac{d}{d\tau} (f_{e_2}(t)) = \dfrac{d}{dt} (f_{e_2}(t)) \dfrac{dt}{d\tau} = - \dfrac{d}{dt} (f_{e_2}(t)) = - f'_{e_2}(t)
\end{equation}

so the coordinate derivative changes sign under reparametrization. Hence, edgewise derivatives are not invariant under orientation changes. By contrast, the outward derivative $\partial_e g(v)$ is invariant, and is therefore the correct intrinsic quantity to check the Kirchhoff condition.

In the compatible orientation case, $f'_{e_1}(\ell_1) = f'_{e_2}(0)$, so the coordinate derivatives match. In the flipped orientation case, $g'_{e_1}(\ell_1) \neq g'_{e_2}(\ell_2)$, but this mismatch is purely a consequence of the reversed parametrization. The correct invariant comparison is \eqref{eq:invariant_c}, which demonstrates that the Kirchhoff condition is intrinsic and independent of edge parametrization.

In conclusion, the apparent contradiction arises only when comparing coordinate derivatives with opposite orientations, which is not geometrically meaningful. Continuity of the derivative at a vertex must be interpreted intrinsically: at a degree-two vertex, this intrinsic continuity is equivalent to the Kirchhoff condition.



```{r}
e2 <- e2[2:1,]
graph <- metric_graph$new(edges = list(e1 = e1, e2 = e2))
graph$build_mesh(h = h)
```


```{r}
e1_ini_x <- -ell1; e1_ini_y <- 0; e1_ini_z <- 0
e1_fin_x <- 0; e1_fin_y <- 0; e1_fin_z <- 0

# Midpoint
xm1 <- (e1_fin_x + e1_ini_x)/2
ym1 <- (e1_fin_y + e1_ini_y)/2
zm1 <- (e1_fin_z + e1_ini_z)/2

# Direction vector
dx1 <- e1_fin_x - e1_ini_x
dy1 <- e1_fin_y - e1_ini_y
dz1 <- e1_fin_z - e1_ini_z

e2_ini_x <- ell2; e2_ini_y <- 0; e2_ini_z <- 0
e2_fin_x <- 0; e2_fin_y <- 0; e2_fin_z <- 0

# Midpoint
xm2 <- (e2_fin_x + e2_ini_x)/2
ym2 <- (e2_fin_y + e2_ini_y)/2
zm2 <- (e2_fin_z + e2_ini_z)/2

# Direction vector
dx2 <- e2_fin_x - e2_ini_x
dy2 <- e2_fin_y - e2_ini_y
dz2 <- e2_fin_z - e2_ini_z
```

```{r}
fe1 <- function(t) t^4
fe2 <- function(t) (t - (ell1 + ell2))^4

dfe1 <- function(t) 4*t^3
dfe2 <- function(t) 4*(t - (ell1 + ell2))^3

ddfe1 <- function(t) 12*t^2
ddfe2 <- function(t) 12*(t - (ell1 + ell2))^2

dddfe1 <- function(t) 24*t
dddfe2 <- function(t) 24*(t - (ell1 + ell2))

f_list <- list(fe1, fe2)
df_list <- list(dfe1, dfe2)
ddf_list <- list(ddfe1, ddfe2)
dddf_list <- list(dddfe1, dddfe2)

f <- my_apply_edge_functions(graph, f_list, ell1, ell2, h)
df <- my_apply_edge_functions(graph, df_list, ell1, ell2, h)
ddf <- my_apply_edge_functions(graph, ddf_list, ell1, ell2, h)
dddf <- my_apply_edge_functions(graph, dddf_list, ell1, ell2, h)

f_aux <- my_apply_edge_functions(graph, f_list_aux, ell1, ell2, h)
```


```{r}
p_base <- graph$plot_function(X = rep(0, nrow(graph$mesh$VtE)), vertex_size = gsw, line_color = "black", edge_width = gsw, line_width = gsw, type = "plotly")
DF <- f$DF
pf3 <- p_base |>
  add_trace(
  type = "cone",
  x = ym1,
  y = xm1,
  z = zm1,
  u = dy1,
  v = dx1,
  w = dz1,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("red", "red")),
  cmin = 0,
  cmax = 1
) |>
  add_trace(
  type = "cone",
  x = ym2,
  y = xm2,
  z = zm2,
  u = dy2,
  v = dx2,
  w = dz2,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("red", "red")),
  cmin = 0,
  cmax = 1
) |>
    add_trace(data = DF,
            x = ~y, 
            y = ~x, 
            z = ~z, 
            type = "scatter3d",
            mode = "lines",  
            line = list(color = "rgb(0,0,200)", width = gsw),
            showlegend = FALSE) |>
  add_trace(x = rep(DF$y, each = 3), 
            y = rep(DF$x, each = 3), 
            z = unlist(lapply(DF$z, function(zj) c(0, zj, NA))),
            type = "scatter3d", 
            mode = "lines",
            line = list(color = "gray", width = 0.5),
            showlegend = FALSE) |>
  config(mathjax = 'cdn') |>
  plotly::layout(title = list(text = TeX("g"), y = 0.8),
                 font = list(family = "Palatino"),
                 scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
                   aspectratio = list(x = 2, 
                                 y = 2, 
                                 z = 2),
                   camera = list(eye = list(x = x_eye, 
                                       y = y_eye, 
                                       z = z_eye),
                            center = list(x = 0, 
                                          y = 0, 
                                          z = 0)),
                   annotations = list(
                     
             list(
               x = e1_ini_y, y = e1_ini_x, z = e1_ini_z,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = 0, y = 0, z = 0,
               text = TeX("v"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = e2_ini_y, y = e2_ini_x, z = e2_ini_z,
               text = TeX("v_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym1, y = xm1, z = zm1,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym2, y = xm2, z = zm2,
               text = TeX("e_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"))
                 ))

DF <- df$DF
pdf3 <- p_base |>
  add_trace(
  type = "cone",
  x = ym1,
  y = xm1,
  z = zm1,
  u = dy1,
  v = dx1,
  w = dz1,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("red", "red")),
  cmin = 0,
  cmax = 1
) |>
  add_trace(
  type = "cone",
  x = ym2,
  y = xm2,
  z = zm2,
  u = dy2,
  v = dx2,
  w = dz2,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("red", "red")),
  cmin = 0,
  cmax = 1
) |>
    add_trace(data = DF,
            x = ~y, 
            y = ~x, 
            z = ~z, 
            type = "scatter3d",
            mode = "lines",  
            line = list(color = "rgb(0,0,200)", width = gsw),
            showlegend = FALSE) |>
  add_trace(x = rep(DF$y, each = 3), 
            y = rep(DF$x, each = 3), 
            z = unlist(lapply(DF$z, function(zj) c(0, zj, NA))),
            type = "scatter3d", 
            mode = "lines",
            line = list(color = "gray", width = 0.5),
            showlegend = FALSE) |>
  config(mathjax = 'cdn') |>
  plotly::layout(title = list(text = TeX("g'"), y = 0.8),
                 font = list(family = "Palatino"),
                 scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
                   aspectratio = list(x = 2, 
                                 y = 2, 
                                 z = 2),
                   camera = list(eye = list(x = x_eye, 
                                       y = y_eye, 
                                       z = z_eye),
                            center = list(x = 0, 
                                          y = 0, 
                                          z = 0)),
                   annotations = list(
                     
             list(
               x = e1_ini_y, y = e1_ini_x, z = e1_ini_z,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = 0, y = 0, z = 0,
               text = TeX("v"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = e2_ini_y, y = e2_ini_x, z = e2_ini_z,
               text = TeX("v_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym1, y = xm1, z = zm1,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym2, y = xm2, z = zm2,
               text = TeX("e_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"))
                 ))

DF <- ddf$DF
pddf3 <- p_base |>
  add_trace(
  type = "cone",
  x = ym1,
  y = xm1,
  z = zm1,
  u = dy1,
  v = dx1,
  w = dz1,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("red", "red")),
  cmin = 0,
  cmax = 1
) |>
  add_trace(
  type = "cone",
  x = ym2,
  y = xm2,
  z = zm2,
  u = dy2,
  v = dx2,
  w = dz2,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("red", "red")),
  cmin = 0,
  cmax = 1
) |>
    add_trace(data = DF,
            x = ~y, 
            y = ~x, 
            z = ~z, 
            type = "scatter3d",
            mode = "lines",  
            line = list(color = "rgb(0,0,200)", width = gsw),
            showlegend = FALSE) |>
  add_trace(x = rep(DF$y, each = 3), 
            y = rep(DF$x, each = 3), 
            z = unlist(lapply(DF$z, function(zj) c(0, zj, NA))),
            type = "scatter3d", 
            mode = "lines",
            line = list(color = "gray", width = 0.5),
            showlegend = FALSE) |>
  config(mathjax = 'cdn') |>
  plotly::layout(title = list(text = TeX("g''"), y = 0.8), 
                 font = list(family = "Palatino"),
                 scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
                   aspectratio = list(x = 2, 
                                 y = 2, 
                                 z = 2),
                   camera = list(eye = list(x = x_eye, 
                                       y = y_eye, 
                                       z = z_eye),
                            center = list(x = 0, 
                                          y = 0, 
                                          z = 0)),
                   annotations = list(
                     
             list(
               x = e1_ini_y, y = e1_ini_x, z = e1_ini_z,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = 0, y = 0, z = 0,
               text = TeX("v"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = e2_ini_y, y = e2_ini_x, z = e2_ini_z,
               text = TeX("v_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym1, y = xm1, z = zm1,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym2, y = xm2, z = zm2,
               text = TeX("e_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"))
                 ))

DF <- dddf$DF
pdddf3 <- p_base |>
  add_trace(
  type = "cone",
  x = ym1,
  y = xm1,
  z = zm1,
  u = dy1,
  v = dx1,
  w = dz1,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("red", "red")),
  cmin = 0,
  cmax = 1
) |>
  add_trace(
  type = "cone",
  x = ym2,
  y = xm2,
  z = zm2,
  u = dy2,
  v = dx2,
  w = dz2,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("red", "red")),
  cmin = 0,
  cmax = 1
) |>
    add_trace(data = DF,
            x = ~y, 
            y = ~x, 
            z = ~z, 
            type = "scatter3d",
            mode = "lines",  
            line = list(color = "rgb(0,0,200)", width = gsw),
            showlegend = FALSE) |>
  add_trace(x = rep(DF$y, each = 3), 
            y = rep(DF$x, each = 3), 
            z = unlist(lapply(DF$z, function(zj) c(0, zj, NA))),
            type = "scatter3d", 
            mode = "lines",
            line = list(color = "gray", width = 0.5),
            showlegend = FALSE) |>
  config(mathjax = 'cdn') |>
  plotly::layout(title = list(text = TeX("g'''"), y = 0.8), 
                 font = list(family = "Palatino"),
                 scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
                   aspectratio = list(x = 2, 
                                 y = 2, 
                                 z = 2),
                   camera = list(eye = list(x = x_eye, 
                                       y = y_eye, 
                                       z = z_eye),
                            center = list(x = 0, 
                                          y = 0, 
                                          z = 0)),
                   annotations = list(
                     
             list(
               x = e1_ini_y, y = e1_ini_x, z = e1_ini_z,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = 0, y = 0, z = 0,
               text = TeX("v"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = e2_ini_y, y = e2_ini_x, z = e2_ini_z,
               text = TeX("v_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym1, y = xm1, z = zm1,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym2, y = xm2, z = zm2,
               text = TeX("e_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"))
                 ))

save(pf3, file = here::here("data_files/pf3.Rdata"))
save(pdf3, file = here::here("data_files/pdf3.Rdata"))
save(pddf3, file = here::here("data_files/pddf3.Rdata"))
save(pdddf3, file = here::here("data_files/pdddf3.Rdata"))
```









:::: {style="display: grid; grid-template-columns: 485px 485px 485px 485px; grid-column-gap: 0px;"}


::: {}

```{r, eval= TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Function $g = \\{g_e\\}_{e\\in\\mathcal{E}}$ given by $g_{e_1}(\\tau) = \\tau^4$ and $g_{e_2}(\\tau) = (\\tau-(\\ell_1+\\ell_2))^4$.")}
load(here::here("data_files/pf3.Rdata"))
pf3
```

:::


::: {}

```{r, eval= TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Function $g' = \\{g'_e\\}_{e\\in\\mathcal{E}}$ given by $g'_{e_1}(\\tau) = 4\\tau^3$ and $g'_{e_2}(\\tau) = 4(\\tau-(\\ell_1+\\ell_2))^3$.")}
load(here::here("data_files/pdf3.Rdata"))
pdf3
```

:::


::: {}

```{r, eval= TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Function $g'' = \\{g''_e\\}_{e\\in\\mathcal{E}}$ given by $g''_{e_1}(\\tau) = 12\\tau^2$ and $g''_{e_2}(\\tau) = 12(\\tau-(\\ell_1+\\ell_2))^2$.")}
load(here::here("data_files/pddf3.Rdata"))
pddf3
```

:::


::: {}

```{r, eval= TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Function $g''' = \\{g'''_e\\}_{e\\in\\mathcal{E}}$ given by $g'''_{e_1}(\\tau) = 24\\tau$ and $g'''_{e_2}(\\tau) = 24(\\tau-(\\ell_1+\\ell_2))$.")}
load(here::here("data_files/pdddf3.Rdata"))
pdddf3
```


:::

::::


Figure 6 illustrates precisely the relation expressed in \eqref{eq:der_inv}. That is, $g'_{e_2}$ can be obtained by multiplying $f'_{e_2}$ by $-1$.

# Even order derivatives are orientation-independent

We again apply the chain rule in \eqref{eq:der_inv} to obtain
\begin{equation}
g''_{e_2}(\tau) = \dfrac{d}{d\tau} ( - f'_{e_2}(t)) = - \dfrac{d}{dt} (f'_{e_2}(t)) \dfrac{dt}{d\tau} = f''_{e_2}(t),
\end{equation}
so that the second derivative does not change sign under a flip. See Figure 7. This means that even order derivatives are orientation-independent. In general, for the $k$-th derivative, we have
\begin{equation}
\dfrac{d^k}{d\tau^k}(g_{e_2}(\tau)) = (-1)^k\dfrac{d^k}{dt^k}(f_{e_2}(t)).
\end{equation}


# Additional plots

```{r}
DF <- f_aux$DF
pf_aux <- p_base |>
  add_trace(
  type = "cone",
  x = ym1,
  y = xm1,
  z = zm1,
  u = dy1,
  v = dx1,
  w = dz1,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("red", "red")),
  cmin = 0,
  cmax = 1
) |>
  add_trace(
  type = "cone",
  x = ym2,
  y = xm2,
  z = zm2,
  u = dy2,
  v = dx2,
  w = dz2,
  sizemode = "absolute",
  sizeref = sizeref,
  showscale = FALSE,
  showlegend = FALSE,
  colorscale = list(c(0, 1), c("red", "red")),
  cmin = 0,
  cmax = 1
) |>
    add_trace(data = DF,
            x = ~y, 
            y = ~x, 
            z = ~z, 
            type = "scatter3d",
            mode = "lines",  
            line = list(color = "rgb(0,0,200)", width = gsw),
            showlegend = FALSE) |>
  add_trace(x = rep(DF$y, each = 3), 
            y = rep(DF$x, each = 3), 
            z = unlist(lapply(DF$z, function(zj) c(0, zj, NA))),
            type = "scatter3d", 
            mode = "lines",
            line = list(color = "gray", width = 0.5),
            showlegend = FALSE) |>
  config(mathjax = 'cdn') |>
  plotly::layout(title = list(text = TeX("\\hat{f}"), y = 0.8),
                 font = list(family = "Palatino"),
                 scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
                   aspectratio = list(x = 2, 
                                 y = 2, 
                                 z = 2),
                   camera = list(eye = list(x = x_eye, 
                                       y = y_eye, 
                                       z = z_eye),
                            center = list(x = 0, 
                                          y = 0, 
                                          z = 0)),
                   annotations = list(
                     
             list(
               x = e1_ini_y, y = e1_ini_x, z = e1_ini_z,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = 0, y = 0, z = 0,
               text = TeX("v"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = e2_ini_y, y = e2_ini_x, z = e2_ini_z,
               text = TeX("v_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym1, y = xm1, z = zm1,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"),
             list(
               x = ym2, y = xm2, z = zm2,
               text = TeX("e_2"),
               textangle = 0, ax = 0, ay = 35,
               font = list(color = "black", size = gfsize),
               arrowcolor = "rgba(0,0,0,0)"))
                 ))

save(pf_aux, file = here::here("data_files/pf_aux.Rdata"))

```


:::: {style="display: grid; grid-template-columns: 485px 485px 485px 485px; grid-column-gap: 0px;"}


::: {}

```{r, eval = TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Function $f = \\{f_e\\}_{e\\in\\mathcal{E}}$ given by $f_{e_1}(t) = t^4$ and $f_{e_2}(t) = (t+\\ell_1)^4$.")}
load(here::here("data_files/pf.Rdata"))
pf
```

:::

::: {}

```{r, eval = TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Function $f = \\{f_e\\}_{e\\in\\mathcal{E}}$ given by $f_{e_1}(t) = t^4$ and $f_{e_2}(t) = (t+\\ell_1)^4$.")}
load(here::here("data_files/pf_aux.Rdata"))
pf_aux
```

:::

::: {}

```{r, eval= TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Function $g = \\{g_e\\}_{e\\in\\mathcal{E}}$ given by $g_{e_1}(\\tau) = \\tau^4$ and $g_{e_2}(\\tau) = (\\tau-(\\ell_1+\\ell_2))^4$.")}
load(here::here("data_files/pf3.Rdata"))
pf3
```

:::

::::

# References

```{r, eval = TRUE}
grateful::cite_packages(output = "paragraph", out.dir = ".")
```

