---
title: "Convergence in 𝑚 for the optimal control variable"
date: "Last modified: `r format(Sys.time(), '%d-%m-%Y.')`"
output:
  html_document:
    mathjax: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
    highlight: pygments
    theme: flatly
    code_folding: hide # class.source = "fold-hide" to hide code and add a button to show it
    df_print: paged
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
    fig_caption: true
    code_download: true
    css: visual.css
always_allow_html: true
bibliography: 
  - references.bib
  - grateful-refs.bib
header-includes:
  - \newcommand{\ar}{\mathbb{R}}
  - \newcommand{\llav}[1]{\left\{#1\right\}}
  - \newcommand{\pare}[1]{\left(#1\right)}
  - \newcommand{\Ncal}{\mathcal{N}}
  - \newcommand{\Vcal}{\mathcal{V}}
  - \newcommand{\Ecal}{\mathcal{E}}
  - \newcommand{\Wcal}{\mathcal{W}}
  - \newcommand{\almosteverywhere}{\mathrm{a.e.}\;}
---

Go back to the [Contents](about.html) page.

<div style="color: #2c3e50; text-align: right;">
********  
<strong>Press Show to reveal the code chunks.</strong>  

********
</div>


```{r}
# Create a clipboard button on the rendered HTML page
source(here::here("clipboard.R")); clipboard
# Set seed for reproducibility
set.seed(1982) 
# Set global options for all code chunks
knitr::opts_chunk$set(
  # Disable messages printed by R code chunks
  message = FALSE,    
  # Disable warnings printed by R code chunks
  warning = FALSE,    
  # Show R code within code chunks in output
  echo = TRUE,        
  # Include both R code and its results in output
  include = TRUE,     
  # Evaluate R code chunks
  eval = TRUE,       
  # Enable caching of R code chunks for faster rendering
  cache = FALSE,      
  # Align figures in the center of the output
  fig.align = "center",
  # Enable retina display for high-resolution figures
  retina = 2,
  # Show errors in the output instead of stopping rendering
  error = TRUE,
  # Do not collapse code and output into a single block
  collapse = FALSE
)
# Start the figure counter
fig_count <- 0
# Define the captioner function
captioner <- function(caption) {
  fig_count <<- fig_count + 1
  paste0("Figure ", fig_count, ": ", caption)
}
```

```{r}
library(MetricGraph)
library(ggplot2)
library(reshape2)
library(dplyr)
library(viridis)
library(plotly)
library(patchwork)
library(slackr)
source("keys.R")
slackr_setup(token = token) # token comes from keys.R
```


# Building the graph object

```{r}
V <- rbind(c(0, 0), c(1, 0), c(1, 1), c(0, 1), c(-1, 1), c(-1, 0), c(0, -1))
E <- rbind(c(1, 2), c(2, 3), c(3, 4), c(4, 5),
           c(5, 6), c(6, 1), c(4, 1),c(1, 7))
graph <- metric_graph$new(V = V, E = E)
```

# Geodesic distance on a metric graph

Follow this [link](functions_on_graph.html#geodesic) for an illustration of the geodesic distance on a metric graph.

# Function on a metric graph

Follow this [link](functions_on_graph.html#functions-def-on-graph) for an illustration of a function on a metric graph.

# Basis functions on a metric graph

Follow this [link](basis_functions_alt_illustrations.html) for alternative illustrations of basis functions on a metric graph.

Let each edge $e\in\Ecal$ be subdivided into $n_{e}\geq 2$ regular segments of length $h_{e}$, and be delimited by the nodes $0 = x_0^{e},x_1^{e},\dots,x_{n_{e}-1}^{e}, x_{n_{e}}^{e} = \ell_{e}$. For each $j = 1,\dots,n_{e}-1$, we consider the following standard hat basis functions 
\begin{equation*}
    \varphi_j^{e}(x)=\begin{cases}
        1-\dfrac{|x_j^{e}-x|}{h_{e}},&\text{ if }x_{j-1}^{e}\leq x\leq x_{j+1}^{e},\\
        0,&\text{ otherwise}.
    \end{cases}
\end{equation*}
For each $e\in\Ecal$, the set of hat functions $\llav{\varphi_1^{e},\dots,\varphi_{n_{e}-1}^{e}}$ is a basis for the space
\begin{equation*}
    V_{h_{e}} = \llav{w\in H_0^1(e)\;\Big|\;\forall j = 0,1,\dots,n_{e}-1:w|_{[x_j^{e}, x_{j+1}^{e}]}\in\mathbb{P}^1},
\end{equation*}
where $\mathbb{P}^1$ is the space of linear functions on $[0,\ell_{e}]$. For each vertex $v\in\Vcal$, we define
\begin{equation*}
    \Ncal_v = \llav{\bigcup_{e\in\llav{e\in\Ecal_v: v = x_0^e}}[v,x_1^e]}\bigcup\llav{\bigcup_{e\in\llav{e\in\Ecal_v: v = x^e_{n_e}}}[x^e_{n_e-1},v]},
\end{equation*}
which is a star-shaped set with center at $v$ and rays made of the segments contiguous to $v$. On $\mathcal{N}_v$, we define the hat functions as
\begin{equation*}
    \phi_v(x)=\begin{cases}
        1-\dfrac{|x_v^{e}-x|}{h_{e}},&\text{ if }x\in\mathcal{N}_v\cap e \text{ and }e\in\Ecal_v,\\
        0,&\text{ otherwise},
    \end{cases}
\end{equation*}
where $x_v^e$ is either $x_0^e$ or $x_{n_e}^e$ depending on the edge direction and its parameterization. See @arioli2018finite for more. Figure 3 below provides an illustration of the system of basis functions $\{\varphi_j^e, \phi_v\}$ together with the set $\Ncal_v$.

<div style="color: blue;">
********
**Press the Show button below to reveal the code.**

********
</div>

```{r, fig.height = 8, out.width = "100%", class.source = "fold-hide", fig.cap = captioner("Illustration of the system of basis functions $\\{\\varphi_j^e, \\phi_v\\}$ (solid gray lines) on the graph $\\Gamma= (\\Vcal,\\Ecal)$, where $\\Ecal= \\llav{e_1,\\dots,e_8}$ and $\\Vcal =  \\llav{v_1,\\dots,v_7}$. Note that for all $e_i\\in\\Ecal$, $n_{e_i} = 3$ and $h_{e_i} = 1/3$. In particular, for edge $e_7$, observe that the three regular segments are delimited by the nodes $v_6 = x_0^{e_7}, x_1^{e_7}, x_2^{e_7}, x_3^{e_7} = v_7$. Corresponding to node $x_1^{e_7}$, we have plotted the basis function $\\varphi_1^{e_7}$ in blue. Notice also that the set $\\Ncal_{v_2}$ is depicted in green and its corresponding basis function $\\phi_{v_2}$ is shown in red.")}
# star set
d49 = data.frame(y = c(1/3,0), x = c(0,0), z = c(0,0))
d50 = data.frame(y = c(0,0), x = c(1/3,0), z = c(0,0))
d51 = data.frame(y = c(-1/3,0), x = c(0,0), z = c(0,0))
d52 = data.frame(y = c(0,0), x = c(-1/3,0), z = c(0,0))

graph_to_get_loc <- graph$clone()
graph_to_get_loc$build_mesh(h = 1/120)

loc <- graph_to_get_loc$get_mesh_locations()

graph$build_mesh(h = 1/3)

A <- graph$fem_basis(loc)

DD <- data.frame(A = as.matrix(A)) %>% 
  rowwise() %>%
  mutate(max_value = max(c_across(everything()))) %>%
  cbind(edge_number = loc[, 1], distance_on_edge = loc[, 2], A.24 = 0)

graph$add_observations(data = DD, edge_number = "edge_number",
  distance_on_edge = "distance_on_edge", data_coords = "PtE", normalized = TRUE, clear_obs = TRUE)

# Initialize the first plot
p <- graph_to_get_loc$plot_function(X = DD[[paste0("A.", 1)]], line_color = "red",
                                     edge_width = 2, line_width = 2, support_width = 0.2, plotly = TRUE)
# Loop through to create the remaining plots
for (i in 2:24) {
  line_color <- "gray"
  if (i == 11) {line_color <- "blue"}
  if (i == 24) {line_color <- "black"}
  X <- DD[[paste0("A.", i)]]
  p <- graph_to_get_loc$plot_function(X = X, line_color = line_color, edge_width = 2, line_width = 2, support_width = 0.2, plotly = TRUE, p = p)
}

pp = p %>%  
  config(mathjax = 'cdn') %>% 
  layout(title = TeX("\\text{Basis functions on a metric graph }\\Gamma = (\\mathcal{V},\\mathcal{E})"), 
         showlegend = FALSE,
                    font = list(family = "Palatino"),
                    scene = list(
                      aspectratio = list(x = 1.8, y = 1.8, z = 0.4),
                      annotations = list(
                        list(
                          x = -1, y = 0, z = 0,
                          text = TeX("v_1"),
                          textangle = 0, ax = 0, ay = 25,
                          font = list(color = "black", size = 16),
                          arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                        list(
                          x = 0, y = 0, z = 0,
                          text = TeX("v_2"),
                          textangle = 0, ax = 0, ay = 25,
                          font = list(color = "black", size = 16),
                          arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                        list(
                          x = 0, y = -1, z = 0,
                          text = TeX("v_3"),
                          textangle = 0, ax = 0, ay = 25,
                          font = list(color = "black", size = 16),
                          arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                        list(
                          x = 1, y = -1, z = 0,
                          text = TeX("v_4"),
                          textangle = 0, ax = 0, ay = 25,
                          font = list(color = "black", size = 16),
                          arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                        list(
                          x = 1, y = 0, z = 0,
                          text = TeX("v_5"),
                          textangle = 0, ax = 0, ay = 25,
                          font = list(color = "black", size = 16),
                          arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                        list(
                          x = 1, y = 1, z = 0,
                          text = TeX("v_6,x_0^{e_7}"),
                          textangle = 0, ax = 0, ay = 25,
                          font = list(color = "black", size = 16),
                          arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                        list(
                          x = 0, y = 1, z = 0,
                          text = TeX("v_7,x_3^{e_7}"),
                          textangle = 0, ax = 0, ay = 25,
                          font = list(color = "black", size = 16),
                          arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                        list(
                          x = 2/3, y = 1, z = 0,
                          text = TeX("x_1^{e_7}"),
                          textangle = 0, ax = 0, ay = 25,
                          font = list(color = "black", size = 16),
                          arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                        list(
                          x = 1/3, y = 1, z = 0,
                          text = TeX("x_2^{e_7}"),
                          textangle = 0, ax = 0, ay = 25,
                          font = list(color = "black", size = 16),
                          arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                        list(
                          x = 0.15, y = 0, z = 0,
                          text = TeX("\\mathcal{N}_{v_2}"),
                          textangle = 0, ax = 0, ay = 25,
                          font = list(color = "green", size = 16),
                          arrowcolor = "white", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                        list(
                          x = 2/3, y = 1, z = 1,
                          text = TeX("\\varphi_1^{e_7}"),
                          textangle = 0, ax = 0, ay = 75,
                          font = list(color = "blue", size = 16),
                          arrowcolor = "white", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                        list(
                          x = 0, y = 0, z = 1,
                          text = TeX("\\phi_{v_2}"),
                          textangle = 0, ax = 0, ay = 75,
                          font = list(color = "red", size = 16),
                          arrowcolor = "white", arrowsize = 1, arrowwidth = 1,arrowhead = 1)
                        ))) %>% 
  add_trace(x = 0, y = 0, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 0, y = 1, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 1, y = 1, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 1, y = 0, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 1, y = -1, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 0, y = -1, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = -1, y = 0, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = -2/3, y = 0, z = 0, mode = "markers", type = "scatter3d", # before this
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = -1/3, y = 0, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 0, y = -1/3, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 0, y = -2/3, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 1/3, y = -1, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 2/3, y = -1, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 0, y = 1/3, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 0, y = 2/3, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>% 
  add_trace(x = 1/3, y = 0, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 2/3, y = 0, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>% 
  add_trace(x = 1/3, y = 1, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 2/3, y = 1, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>% 
  add_trace(x = 1, y = 1/3, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 1, y = 2/3, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>% 
  add_trace(x = 1, y = -1/3, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>%
  add_trace(x = 1, y = -2/3, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "blue", symbol = 104)) %>% 
  add_trace(data = d49, x = ~x, y = ~y, z = ~z, mode = "lines", type = "scatter3d",
            line = list(width = 3, color = "green", symbol = 104)) %>% 
  add_trace(data = d50, x = ~x, y = ~y, z = ~z, mode = "lines", type = "scatter3d",
            line = list(width = 3, color = "green", symbol = 104)) %>% 
  add_trace(data = d51, x = ~x, y = ~y, z = ~z, mode = "lines", type = "scatter3d",
            line = list(width = 3, color = "green", symbol = 104)) %>% 
  add_trace(data = d52, x = ~x, y = ~y, z = ~z, mode = "lines", type = "scatter3d",
            line = list(width = 3, color = "green", symbol = 104))

pp
```


# References

```{r}
grateful::cite_packages(output = "paragraph", out.dir = ".")
```
