---
title: "Graphs"
date: "Last modified: `r format(Sys.time(), '%d-%m-%Y.')`"
output:
  html_document:
    mathjax: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
    highlight: pygments
    theme: flatly
    code_folding: hide # class.source = "fold-hide" to hide code and add a button to show it
    df_print: paged
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
    fig_caption: true
    code_download: true
    css: visual.css
always_allow_html: true
bibliography: 
  - references.bib
  - grateful-refs.bib
header-includes:
  - \newcommand{\ar}{\mathbb{R}}
  - \newcommand{\llav}[1]{\left\{#1\right\}}
  - \newcommand{\pare}[1]{\left(#1\right)}
  - \newcommand{\Ncal}{\mathcal{N}}
  - \newcommand{\Vcal}{\mathcal{V}}
  - \newcommand{\Ecal}{\mathcal{E}}
  - \newcommand{\Wcal}{\mathcal{W}}
  - \newcommand{\almosteverywhere}{\mathrm{a.e.}\;}
---

Go back to the [Contents](about.html) page.

<div style="color: #2c3e50; text-align: right;">
********  
<strong>Press Show to reveal the code chunks.</strong>  

********
</div>


```{r}
# Create a clipboard button on the rendered HTML page
source(here::here("clipboard.R")); clipboard
# Set seed for reproducibility
set.seed(1982) 
# Set global options for all code chunks
knitr::opts_chunk$set(
  # Disable messages printed by R code chunks
  message = FALSE,    
  # Disable warnings printed by R code chunks
  warning = FALSE,    
  # Show R code within code chunks in output
  echo = TRUE,        
  # Include both R code and its results in output
  include = TRUE,     
  # Evaluate R code chunks
  eval = TRUE,       
  # Enable caching of R code chunks for faster rendering
  cache = FALSE,      
  # Align figures in the center of the output
  fig.align = "center",
  # Enable retina display for high-resolution figures
  retina = 2,
  # Show errors in the output instead of stopping rendering
  error = TRUE,
  # Do not collapse code and output into a single block
  collapse = FALSE
)
# Start the figure counter
fig_count <- 0
# Define the captioner function
captioner <- function(caption) {
  fig_count <<- fig_count + 1
  paste0("Figure ", fig_count, ": ", caption)
}

```

```{r}
library(MetricGraph)
library(ggplot2)
library(reshape2)
library(dplyr)
library(viridis)
library(plotly)
library(patchwork)
library(slackr)
source("keys.R")
slackr_setup(token = token) # token comes from keys.R
```


```{r}
capture.output(
  knitr::purl(here::here("functionality1.Rmd"), output = here::here("functionality1.R")),
  file = here::here("old/purl_log.txt")
)
source(here::here("functionality1.R"))
```

# Basis functions on a metric graph

Let each edge $e\in\Ecal$ be subdivided into $n_{e}\geq 2$ regular segments of length $h_{e}$, and be delimited by the nodes $0 = x_0^{e},x_1^{e},\dots,x_{n_{e}-1}^{e}, x_{n_{e}}^{e} = \ell_{e}$. For each $j = 1,\dots,n_{e}-1$, we consider the following standard hat basis functions 
\begin{equation*}
    \varphi_j^{e}(x)=\begin{cases}
        1-\dfrac{|x_j^{e}-x|}{h_{e}},&\text{ if }x_{j-1}^{e}\leq x\leq x_{j+1}^{e},\\
        0,&\text{ otherwise}.
    \end{cases}
\end{equation*}
For each $e\in\Ecal$, the set of hat functions $\llav{\varphi_1^{e},\dots,\varphi_{n_{e}-1}^{e}}$ is a basis for the space
\begin{equation*}
    V_{h_{e}} = \llav{w\in H_0^1(e)\;\Big|\;\forall j = 0,1,\dots,n_{e}-1:w|_{[x_j^{e}, x_{j+1}^{e}]}\in\mathbb{P}^1},
\end{equation*}
where $\mathbb{P}^1$ is the space of linear functions on $[0,\ell_{e}]$. For each vertex $v\in\Vcal$, we define
\begin{equation*}
    \Ncal_v = \llav{\bigcup_{e\in\llav{e\in\Ecal_v: v = x_0^e}}[v,x_1^e]}\bigcup\llav{\bigcup_{e\in\llav{e\in\Ecal_v: v = x^e_{n_e}}}[x^e_{n_e-1},v]},
\end{equation*}
which is a star-shaped set with center at $v$ and rays made of the segments contiguous to $v$. On $\mathcal{N}_v$, we define the hat functions as
\begin{equation*}
    \phi_v(x)=\begin{cases}
        1-\dfrac{|x_v^{e}-x|}{h_{e}},&\text{ if }x\in\mathcal{N}_v\cap e \text{ and }e\in\Ecal_v,\\
        0,&\text{ otherwise},
    \end{cases}
\end{equation*}
where $x_v^e$ is either $x_0^e$ or $x_{n_e}^e$ depending on the edge direction and its parameterization. See @arioli2018finite for more. Figure 3 below provides an illustration of the system of basis functions $\{\varphi_j^e, \phi_v\}$ together with the set $\Ncal_v$.

<div style="color: blue;">
********
**Press the Show button below to reveal the code.**

********
</div>

```{r}
gets_graph_interval <- function(n){
  edge <- rbind(c(0,0),c(1,0))
  edges = list(edge)
  graph <- metric_graph$new(edges = edges)
  graph$build_mesh(n = n)
  return(graph)
}

n = 3#333
graph = gets_graph_interval(n = n)

notes1 <- list(annotations = list(
             list(
               x = 0, y = 0, z = 0,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = -25,
               font = list(color = "black", size = 14),
               arrowcolor = "black", arrowsize = 1, arrowwidth = 1, arrowhead = 1),
             list(
               x = 0, y = 1, z = 0,
               text = TeX("v_2"),
               textangle = 0, ax = 0, ay = -25,
               font = list(color = "black", size = 14),
               arrowcolor = "black", arrowsize = 1, arrowwidth = 1, arrowhead = 1),
             list(
               x = 0, y = 0.5, z = 0,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 25,
               font = list(color = "black", size = 14),
               arrowcolor = "white", arrowsize = 1, arrowwidth = 1, arrowhead = 1)))

layout1 <- list(camera = list(eye = list(x = 2.3, 
                                       y = 2.3, 
                                       z = 2.3),
                            center = list(x = 0, 
                                          y = 0, 
                                          z = 0)))

p11 <- graph$plot_function(rep(0,nrow(graph$mesh$V)), type = "plotly", line_width = 3, edge_width = 3, line_color = "black")|>
  config(mathjax = 'cdn') |>
  layout(scene =  c(notes1, layout1),
         showlegend = FALSE,
         font = list(family = "Palatino"))
```


```{r}
gets_graph_circle <- function(n){
  r = 1/(pi)
  theta <- seq(from=-pi,to=pi,length.out = 100)
  edge <- cbind(1+r+r*cos(theta),r*sin(theta))
  edges = list(edge)
  graph <- metric_graph$new(edges = edges)
  graph$build_mesh(n = n)
  return(graph)
}
n = 6#666
# Get the graph and build the mesh
graph = gets_graph_circle(n = n)


notes1 <- list(annotations = list(
             list(
               x = 0, y = 1, z = 0,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = -25,
               font = list(color = "black", size = 14),
               arrowcolor = "black", arrowsize = 1, arrowwidth = 1, arrowhead = 1),
             list(
               x = 0, y = 1 + 2/pi, z = 0,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 25,
               font = list(color = "black", size = 14),
               arrowcolor = "white", arrowsize = 1, arrowwidth = 1, arrowhead = 1)))
  
  
p22 <- graph$plot_function(rep(0,nrow(graph$mesh$V)), type = "plotly", line_width = 3, edge_width = 3, line_color = "black") %>% 
  config(mathjax = 'cdn') %>% 
  layout(scene =  c(notes1, layout1),
         showlegend = FALSE,
         font = list(family = "Palatino"))
```


```{r}
gets_graph_tadpole <- function(h){
  edge1 <- rbind(c(0,0),c(1,0))
  theta <- seq(from=-pi,to=pi,length.out = 100)
  edge2 <- cbind(1+1/pi+cos(theta)/pi,sin(theta)/pi)
  edges = list(edge1, edge2)
  graph <- metric_graph$new(edges = edges)
  graph$build_mesh(h = h)
  return(graph)
}
h = 0.3#0.003

# Get the graph and build the mesh
graph = gets_graph_tadpole(h = h)

notes1 <- list(annotations = list(
             list(
               x = 0, y = 0, z = 0,
               text = TeX("v_1"),
               textangle = 0, ax = 0, ay = -25,
               font = list(color = "black", size = 14),
               arrowcolor = "black", arrowsize = 1, arrowwidth = 1, arrowhead = 1),
             list(
               x = -0.03, y = 1.03, z = 0,
               text = TeX("v_2"),
               textangle = 0, ax = 0, ay = -25,
               font = list(color = "black", size = 14),
               arrowcolor = "black", arrowsize = 1, arrowwidth = 1, arrowhead = 1),
             list(
               x = 0, y = 0.5, z = 0,
               text = TeX("e_1"),
               textangle = 0, ax = 0, ay = 25,
               font = list(color = "black", size = 14),
               arrowcolor = "white", arrowsize = 1, arrowwidth = 1, arrowhead = 1),
             list(
               x = 0, y = 1.63, z = 0,
               text = TeX("e_2"),
               textangle = 0, ax = 0, ay = 25,
               font = list(color = "black", size = 14),
               arrowcolor = "white", arrowsize = 1, arrowwidth = 1, arrowhead = 1)))

p33 <- graph$plot_function(rep(0,nrow(graph$mesh$V)), type = "plotly", line_width = 3, edge_width = 3, line_color = "black") %>% 
  config(mathjax = 'cdn') %>% 
  layout(scene =  c(notes1, layout1),
         showlegend = FALSE,
         font = list(family = "Palatino"))
```


```{r}
graph <- gets.graph.tadpole(h = 1/4)
graph_to_get_loc <- gets.graph.tadpole(h = 1/40)
loc <- graph_to_get_loc$get_mesh_locations()


A <- as.matrix(graph$fem_basis(loc))
A <- apply(A, 2, function(x) plotting.order(x, graph_to_get_loc))
A <- rbind(A, rep(NA, ncol(A))) # Add a row of NAs for the plotting

x_g <- graph_to_get_loc$mesh$V[, 1]
y_g <- graph_to_get_loc$mesh$V[, 2]
x <- c(plotting.order(x_g, graph_to_get_loc), NA)
y <- c(plotting.order(y_g, graph_to_get_loc), NA)

x_range <- range(x, na.rm = TRUE)
y_range <- range(y, na.rm = TRUE)
z_range <- c(0,1)
```

```{r}
notes1 <- list(annotations = list(
                   list(
                     x = 0, y = 0, z = 0,
                     text = TeX("v_1"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 1, y = 0, z = 0,
                     text = TeX("v_2"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 0.5, y = 0, z = 0,
                     text = TeX("e_1"),
                     textangle = 0, ax = 0, ay = 25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "white", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 1.63, y = 0, z = 0,
                     text = TeX("e_2"),
                     textangle = 0, ax = 0, ay = 25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "white", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 0.25, y = 0, z = 0,
                     text = TeX("s_1"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 1+1/pi, y = 1/pi-0.01, z = 0,
                     text = TeX("s_2"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1)))
     

df1 <- data.frame(x = c(0.25,1), y = c(0,0), z = c(0,0))
theta <- seq(from=pi/2,to=pi,length.out = 10000)

df2 <- data.frame(x = 1+1/pi+cos(theta)/pi, y = sin(theta)/pi, z = rep(0, length(theta)))
# Start plot
p1 <- plot_ly() |> 
  config(mathjax = 'cdn') |>
  add_trace(x = x, 
            y = y, 
            z = x*0, 
            type = "scatter3d",
            mode = "lines",  
            line = list(color = "black", width = 3),
            showlegend = FALSE) |>
  add_trace(x = 0, y = 0, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "black", symbol = 104),
            showlegend = FALSE) |>
  add_trace(x = 1, y = 0, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "black", symbol = 104),
            showlegend = FALSE) |>
  add_trace(x = 0.25, y = 0, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 5, color = "red", symbol = 104),
            showlegend = FALSE) |> 
  add_trace(x = 1+1/pi, y = 1/pi, z = 0, mode = "markers", type = "scatter3d", 
            marker = list(size = 5, color = "red", symbol = 104),
            showlegend = FALSE) |> 
  add_trace(data = df1, x = ~x, y = ~y, z = ~z, mode = "lines", type = "scatter3d",
            line = list(width = 4, color = "red", symbol = 104),
            showlegend = FALSE) |>
  add_trace(data = df2, x = ~x, y = ~y, z = ~z, mode = "lines", type = "scatter3d",
            line = list(width = 4, color = "red", symbol = 104),
            showlegend = FALSE) |>
  layout(scene = c(tadpole.layout(x_range, y_range, z_range),notes1),
         showlegend = FALSE,
         font = list(family = "Palatino"))
```



```{r}
df3 <- data.frame(x = graph$mesh$V[, 1], y = graph$mesh$V[, 2], z = rep(0, length(graph$mesh$V[, 1])))


df4 <- df3[6:nrow(df3), ]


notes2 <- list(annotations = list(
                   list(
                     x = 0, y = 0, z = 0,
                     text = TeX("v_1"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 1, y = 0, z = 0,
                     text = TeX("v_2"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = df4[1,1], y = df4[1,2], z = 0,
                     text = TeX("x_1^{e_2}"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = df4[2,1], y = df4[2,2], z = 0,
                     text = TeX("x_2^{e_2}"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = df4[3,1], y = df4[3,2], z = 0,
                     text = TeX("x_3^{e_2}"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = df4[4,1], y = df4[4,2], z = 0,
                     text = TeX("x_4^{e_2}"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = df4[5,1], y = df4[5,2], z = 0,
                     text = TeX("x_5^{e_2}"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = df4[6,1], y = df4[6,2], z = 0,
                     text = TeX("x_6^{e_2}"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = df4[7,1], y = df4[7,2], z = 0,
                     text = TeX("x_7^{e_2}"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 0.25, y = 0, z = 0,
                     text = TeX("x_1^{e_1}"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 0.5, y = 0, z = 0,
                     text = TeX("x_2^{e_1}"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 0.75, y = 0, z = 0,
                     text = TeX("x_3^{e_1}"),
                     textangle = 0, ax = 0, ay = -25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1)))

p2 <- plot_ly() |> 
  config(mathjax = 'cdn') |>
  add_trace(x = x, 
            y = y, 
            z = x*0, 
            type = "scatter3d",
            mode = "lines",  
            line = list(color = "black", width = 3),
            showlegend = FALSE) |>
  add_trace(data = df3, x = ~x, y = ~y, z = ~z, mode = "markers", type = "scatter3d", 
            marker = list(size = 4, color = "gray", symbol = 104)) |>
  layout(scene = c(tadpole.layout(x_range, y_range, z_range), notes2),
         showlegend = FALSE,
         font = list(family = "Palatino"))
```


```{r}
notes3 <- list(annotations = list(
                   list(
                     x = 0, y = 0, z = 1,
                     text = TeX("\\phi_{v_1}"),
                     textangle = 0, ax = 0, ay = -15,
                     font = list(color = "red", size = 16),
                     arrowcolor = "white", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 0, y = 0, z = 0,
                     text = TeX("\\mathcal{N}_{v_1}"),
                     textangle = 0, ax = 25, ay = 5,
                     font = list(color = "green", size = 20),
                     arrowcolor = "white", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 1, y = 0, z = 1,
                     text = TeX("\\phi_{v_2}"),
                     textangle = 0, ax = 0, ay = -15,
                     font = list(color = "red", size = 16),
                     arrowcolor = "white", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 0, y = 0, z = 0,
                     text = TeX("v_1"),
                     textangle = 0, ax = 0, ay = 25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 1, y = 0, z = 0,
                     text = TeX("v_2"),
                     textangle = 0, ax = 0, ay = 25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = 1, y = 0, z = 0,
                     text = TeX("\\mathcal{N}_{v_2}"),
                     textangle = 0, ax = 40, ay = -10,
                     font = list(color = "green", size = 20),
                     arrowcolor = "white", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = df4[5,1], y = df4[5,2], z = 0,
                     text = TeX("x_5^{e_2}"),
                     textangle = 0, ax = 0, ay = 25,
                     font = list(color = "black", size = 14),
                     arrowcolor = "black", arrowsize = 1, arrowwidth = 1,arrowhead = 1),
                   list(
                     x = df4[5,1], y = df4[5,2], z = 1,
                     text = TeX("\\varphi_5^{e_2}"),
                     textangle = 0, ax = 0, ay = -15,
                     font = list(color = "blue", size = 20),
                     arrowcolor = "white", arrowsize = 1, arrowwidth = 1,arrowhead = 1)))

p3 <- plot_ly() |> 
  config(mathjax = 'cdn') |>
  add_trace(x = rep(x, times = graph$nV), 
            y = rep(y, times = graph$nV), 
            z = as.vector(A[, 1:graph$nV]), 
            type = "scatter3d", 
            mode = "lines",
            line = list(color = "red", width = 3), 
            showlegend = FALSE) |>
  add_trace(x = rep(x, times = ncol(A) - graph$nV), 
            y = rep(y, times = ncol(A) - graph$nV), 
            z = as.vector(A[, (graph$nV+1):ncol(A)]), 
            type = "scatter3d",
            mode = "lines", 
            line = list(color = "darkgray", width = 3), 
            showlegend = FALSE) |>
  add_trace(x = rep(x, each = 3), 
            y = rep(y, each = 3), 
            z = unlist(lapply(apply(A, 1, max, na.rm = TRUE), function(zj) c(0, zj, NA))),
            type = "scatter3d", 
            mode = "lines",
            line = list(color = "lightgray", width = 0.5),
            showlegend = FALSE) |>
  add_trace(x = x, 
            y = y, 
            z = as.vector(A[, 10]), 
            type = "scatter3d",
            mode = "lines",  
            line = list(color = "blue", width = 3),
            showlegend = FALSE) |>
  add_trace(x = x, 
            y = y, 
            z = x*0, 
            type = "scatter3d",
            mode = "lines",  
            line = list(color = "black", width = 3),
            showlegend = FALSE) |>
  add_trace(x = rep(x, times = graph$nV), 
            y = rep(y, times = graph$nV), 
            z = c(replace(rep(NA, nrow(A)), 1:11, 0), 
                  replace(rep(NA, nrow(A)), c(31:51, 111:121), 0)), 
            type = "scatter3d", 
            mode = "lines",
            line = list(color = "green", width = 3), 
            showlegend = FALSE) |>
  layout(scene = c(tadpole.layout(x_range, y_range, z_range), notes3),
         showlegend = FALSE,
         font = list(family = "Palatino"))
```


# Just the graphs

:::: {style="display: grid; grid-template-columns: 400px 400px 400px; grid-column-gap: 0px;"}


::: {}

```{r, fig.height = 6, out.width = "100%", fig.cap = captioner("Exact and approximated covariance function on the interval graph.")}
p11
```

:::


::: {}

```{r, fig.height = 6, out.width = "100%", fig.cap = captioner("Exact and approximated covariance function on the circle graph.")}
p22
```


:::



::: {}


```{r, fig.height = 6, out.width = "100%", fig.cap = captioner("Exact and approximated covariance function on the tadpole graph.")}
p33
```


:::


::::


# More than just the graphs

:::: {style="display: grid; grid-template-columns: 400px 400px 400px; grid-column-gap: 0px;"}


::: {}

```{r, fig.height = 6, out.width = "100%", fig.cap = captioner("Exact and approximated covariance function on the interval graph.")}
p1
```

:::


::: {}

```{r, fig.height = 6, out.width = "100%", fig.cap = captioner("Exact and approximated covariance function on the circle graph.")}
p2
```


:::



::: {}


```{r, fig.height = 6, out.width = "100%", fig.cap = captioner("Exact and approximated covariance function on the tadpole graph.")}
p3
```


:::


::::


# References

```{r}
grateful::cite_packages(output = "paragraph", out.dir = ".")
```
