---
title: "Computing the marginal standard deviation explicitly and computationally efficiently"
date: "Last modified: `r format(Sys.time(), '%d-%m-%Y.')`"
output:
  html_document:
    mathjax: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
    highlight: pygments
    theme: flatly
    code_folding: hide # class.source = "fold-hide" to hide code and add a button to show it
    df_print: paged
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
    fig_caption: true
    code_download: true
    css: visual.css
always_allow_html: true
bibliography: 
  - references.bib
  - grateful-refs.bib
header-includes:
  - \newcommand{\ar}{\mathbb{R}}
  - \newcommand{\llav}[1]{\left\{#1\right\}}
  - \newcommand{\pare}[1]{\left(#1\right)}
  - \newcommand{\Ncal}{\mathcal{N}}
  - \newcommand{\Vcal}{\mathcal{V}}
  - \newcommand{\Ecal}{\mathcal{E}}
  - \newcommand{\Wcal}{\mathcal{W}}
  - \newcommand{\almosteverywhere}{\mathrm{a.e.}\;}
---

Go back to the [Contents](about.html) page.

<div style="color: #2c3e50; text-align: right;">
********  
<strong>Press Show to reveal the code chunks.</strong>  

********
</div>


Below we set some global options for all code chunks in this document.


```{r}
# Create a clipboard button on the rendered HTML page
source(here::here("clipboard.R")); clipboard
# Set seed for reproducibility
set.seed(593) 
# Set global options for all code chunks
knitr::opts_chunk$set(
  # Disable messages printed by R code chunks
  message = FALSE,    
  # Disable warnings printed by R code chunks
  warning = FALSE,    
  # Show R code within code chunks in output
  echo = TRUE,        
  # Include both R code and its results in output
  include = TRUE,     
  # Evaluate R code chunks
  eval = FALSE,       
  # Enable caching of R code chunks for faster rendering
  cache = FALSE,      
  # Align figures in the center of the output
  fig.align = "center",
  # Enable retina display for high-resolution figures
  retina = 2,
  # Show errors in the output instead of stopping rendering
  error = TRUE,
  # Do not collapse code and output into a single block
  collapse = FALSE
)
# Start the figure counter
fig_count <- 0
# Define the captioner function
captioner <- function(caption) {
  fig_count <<- fig_count + 1
  paste0("Figure ", fig_count, ": ", caption)
}
# Define the function to truncate a number to two decimal places
truncate_to_two <- function(x) {
  truncated <- floor(x * 100) / 100
  sprintf("%.2f", truncated)
}
```


Below we load the necessary libraries and define the auxiliary functions.

```{r, eval = TRUE}
library(rSPDE)
library(MetricGraph)
library(sp)

library(dplyr)
library(plotly)
library(scales)
library(patchwork)
library(tidyr)

library(here)
library(rmarkdown)
# Cite all loaded packages
library(grateful)

library(slackr)
source("keys.R")
slackr_setup(token = token) # token comes from keys.R
```


```{r}
capture.output(
  knitr::purl(here::here("functionality1.Rmd"), output = here::here("functionality1.R")),
  file = here::here("old/purl_log.txt")
)
source(here::here("functionality1.R"))
```

Again, recall the SPDE
\begin{equation}
\label{eq:spde}
\tag{1}
(\kappa^2 - \Delta_{\Gamma})^{\alpha/2}(\tau u) = \mathcal{W}, \quad \text{on $\Gamma$},
\end{equation}
where $\tau$ and $\kappa$ are non constant.

# Variance-stationary Whittle--Matérn fields

One feature of the Whittle--Matérn fields on metric graphs is that they are inherently non-isotropic (@Bolin2024Gaussian). Their marginal variances and practical correlation ranges change over the graph even if $\kappa$ and $\tau$ are constants. That the practical correlation range is non-stationary is often realistic for applications (@Bolin2024Gaussian). However, a non-constant variance might be less ideal in some applications. An example of the marginal standard deviations of a Whittle--Matérn field with $\alpha=1$, $\kappa=2$, and $\tau=1$, on a simple graph are shown in Figure 1. One can note that the variance is higher close to vertices of degree $1$ and lower close to vertices of degree larger than two. 

An interesting option to mitigate this effect is a nonstationary model defined via 
\begin{equation}
\label{eq:spde_variance_stat}
\tag{2}
    (\kappa^2 - \Delta_{\Gamma})^{\alpha/2} (\sigma_{\kappa} u) = \sigma_0 \mathcal{W}, \quad \text{on } \Gamma,
\end{equation}
where $\sigma_0 > 0$ and $\alpha > 1/2$ are constants, $\kappa$ satisfies Assumption 1, and $\sigma_{\kappa}(s)$ represents the marginal standard deviations of a generalized Whittle--Matérn field with the same $\kappa$ and $\alpha$, but with $\tau = 1$. This is a special case of \eqref{eq:spde} with $\tau(s) = \sigma_0^{-1} \sigma_{\kappa}(s)$. Under this specification, the model parameters are $(\kappa, \sigma_0, \alpha)$, and it follows directly that the variance of $u(s)$ is $\sigma_0^2$ for all $s \in \Gamma$. Indeed, letting $v$ denote the generalized Whittle--Matérn field with marginal standard deviations $\sigma_{\kappa}(s)$, by \eqref{eq:spde_variance_stat}, we have $v = \sigma^{-1}_0\sigma_\kappa u$. Since $\mathbb{V}(v(s)) = \sigma_\kappa^2(s)$, it follows that
$$
\mathbb{V}(u(s)) = \mathbb{V}(\sigma_0\sigma_\kappa^{-1}(s)v(s)) = \sigma_0^2\sigma_\kappa^{-2}(s)\mathbb{V}(v(s)) = \sigma_0^2\sigma_\kappa^{-2}(s)\sigma_\kappa^{2}(s) = \sigma_0^2.
$$
For this reason, we refer to this model as a variance-stationary Whittle--Matérn field. Figure 2 illustrates the marginal variance of the field for $\sigma_0 = 1$, showing that the variance is indeed 1 across all locations.


```{r}
rtilde_matern_interval <- function(kappa, tau, le, t1, t2) (1 / (2 * kappa * tau^2 * sinh(kappa * le))) * (cosh(kappa * (le - abs(t1 - t2))) + cosh(kappa * (t1 + t2 - le)))
sparse_A <- function(n) bandSparse(n-1, n, k = c(0, 1), diagonals = list(rep(1, n), rep(-1, n - 1)))
```

Let's build a small graph to illustrate how to compute the marginal standard deviation.


```{r}
a <- 3
b <- 12
edge2_x <- runif(1, 8, 12)

edge1 <- rbind(c(0,0),c(-runif(1, a, b),0))
edge2 <- rbind(c(0,0),c(edge2_x,0))
edge3 <- rbind(c(edge2_x,0),c(edge2_x + runif(1, a, b),0))
edge4 <- rbind(c(edge2_x,0),c(edge2_x + runif(1, a, b),-runif(1, a, b)))
edge5 <- rbind(c(edge2_x,0),c(edge2_x + runif(1, a, b),runif(1, a, b)))
edge6 <- rbind(c(0,0),c(-runif(1, a, b),-runif(1, a, b)))
edge7 <- rbind(c(0,0),c(-runif(1, a, b), runif(1, a, b)))

edges <- list(edge1, edge2, edge3, edge4, edge5, edge6, edge7)
graph <- metric_graph$new(edges = edges)
graph_copy <- graph$clone()
graph_copy2 <- graph$clone()
```


```{r}
h <- 0.1
graph$build_mesh(h = h)
graph_copy2$build_mesh(h = h)
```


```{r}
range <- 1
nu <- 1/2

kappa <- sqrt(8*nu)/range
tau <- 1
sigma <- sqrt(gamma(nu) / (tau^2 * kappa^(2*nu) * (4*pi)^(1/2) * gamma(nu + 1/2)))
alpha <- nu + 1/2 #alpha = 1

rtilde_int <- function(t1, t2, le) rtilde_matern_interval(kappa = kappa, tau = tau, le, t1, t2)
```

# Checking constant variance for variance-stationary Whittle--Matérn fields (without FEM approximation)

```{r}
get_marginal_std <- function(kappa, tau, graph){
  
  V <- graph$V
  E <- graph$E
  degrees <- graph$get_degrees() 
  edge_lengths <- as.vector(graph$get_edge_lengths())
  VtE <- graph$mesh$VtE
  
  
  if(nrow(V) == 2 & nrow(E) == 1){
    aux_function <- function(VtErow) {
      edge <- VtErow[1]
      s <- VtErow[2]
      le <- edge_lengths[edge]
      return(rtilde_int(le*s, le*s, le))
  }
  } else {
    # Build matrix U
    U <- matrix(nrow = 0, ncol = 2)
    for (vertex in seq_len(nrow(V))) {
      if (degrees[vertex] > 1) {
        edges_leaving <- cbind(which(E[,1] %in% vertex), 0) 
        edges_entering <- cbind(which(E[,2] %in% vertex), 1) 
        if (sum(dim(edges_leaving)) == 2 ) {edges_leaving <- NULL}
        if (sum(dim(edges_entering)) == 2 ) {edges_entering <- NULL}
        constraints <- rbind(edges_leaving, edges_entering)
        ordered_constraints <- constraints[order(constraints[, 1], constraints[, 2]),]
        U <- rbind(U, ordered_constraints)
      }
    }
    # Build matrix A
    A <- bdiag(lapply(degrees[degrees >1], sparse_A))
    # Build matrix Sigma
    edge_lengths_in_U <- edge_lengths[U[, 1]] 
    s_diag <- edge_lengths_in_U*U[, 2] 
    diag <- as.vector(mapply(rtilde_int, t1 = s_diag, t2 = s_diag, le = edge_lengths_in_U))
    Sigma <- Diagonal(x = diag)
    for (edge in seq_len(nrow(E))) {
      pos <- which(U[, 1] == edge)
      if (length(pos) > 1) {
        Sigma[pos[1], pos[2]] <- Sigma[pos[2], pos[1]] <- rtilde_int(t1 = 0, t2 = edge_lengths[edge], le = edge_lengths[edge])
      }
    }
  
    ASigmaAt <- A %*% Sigma %*% t(A)
    
    aux_function <- function(VtErow) {
      edge <- VtErow[1]
      s <- VtErow[2]
      le <- edge_lengths[edge]
      pos <- which(U[, 1] == edge)
      cc <- mapply(rtilde_int, t1 = le*s, t2 = U[pos,2]*le, le = le)
      v <- if(length(pos) == 1) as.vector(A[, pos] * cc) else as.vector(A[, pos] %*% cc)
      return(rtilde_int(le*s, le*s, le) - t(v) %*% solve(ASigmaAt, v))
    }
  }
  return(sqrt(apply(X = VtE, MARGIN = 1, FUN = aux_function)))
}
```



```{r}
std_cheap <- get_marginal_std(kappa = kappa, tau = tau, graph = graph)
```

```{r}
mesh_loc <- graph$get_mesh_locations() %>% 
  as.data.frame() %>% 
  mutate(y = 1) %>% 
  rename(edge_number = V1, distance_on_edge = V2)

graph_copy$add_observations(mesh_loc,
                       edge_number = "edge_number",
                       distance_on_edge = "distance_on_edge",
                       data_coords = "PtE",
                       normalized = TRUE, 
                       clear_obs = TRUE)
graph_copy$observation_to_vertex()

Q <- spde_precision(kappa = kappa,
               tau = tau,
               alpha = alpha,
               graph = graph_copy,
               BC = 0) # BC = 1

Sigma <- solve(Q)
std_expensive <- sqrt(diag(Sigma))

nonstat_cov <-  Matrix::Diagonal(x = 1/std_cheap)%*% Sigma %*%Matrix::Diagonal(x = 1/std_cheap)
nonstat_est_sigma <- sqrt(Matrix::diag(nonstat_cov))

sum(abs(std_cheap - std_expensive))
plot(std_cheap - std_expensive)
```

```{r}
a = 2.8
msdwmf <- graph$plot_function(X = std_cheap, vertex_size = 1, type = "plotly", line_color = "#0000C8", line_width = gsw, edge_color = "black", edge_width = gsw) %>% # approx one
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("\\sigma_{\\kappa}(\\cdot)"), y = 0.8),
         font = list(family = "Palatino"),
         margin = list(l = 0, r = 0, b = 0, t = 0),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1, y = 1, z = 1),
camera = list(
      eye = list(x = -0.7*a, y = 0.7*a, z = 0.7*a))))


msdvswmf <- graph$plot_function(X = nonstat_est_sigma, vertex_size = 1, type = "plotly", line_color = "darkgreen", line_width = gsw, edge_color = "black", edge_width = gsw) %>%  
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("\\sigma_0"), y = 0.8),
         font = list(family = "Palatino"),
         margin = list(l = 0, r = 0, b = 0, t = 0),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1, y = 1, z = 1),
camera = list(
      eye = list(x = -0.7*a, y = 0.7*a, z = 0.7*a))))

save(msdwmf, file = here::here("data_files/msdwmf.Rdata"))
save(msdvswmf, file = here::here("data_files/msdvswmf.Rdata"))
```


The following are the plots for the marginal standard deviation.

:::: {style="display: grid; grid-template-columns: 485px 485px 485px; grid-column-gap: 0px;"}


::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Marginal standard deviation $\\sigma_\\kappa(\\cdot)$ of a Whittle--Matérn field with $\\tau = 1$.")}
load(here::here("data_files/msdwmf.Rdata"))
msdwmf
```


:::


::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Marginal standard deviation $\\sigma_0$ of a Generalized Whittle--Matérn field with $\\tau(\\cdot) = \\sigma_\\kappa(\\cdot)$.")}
load(here::here("data_files/msdvswmf.Rdata"))
msdvswmf
```


:::



::::


# Checking constant variance for variance-stationary Whittle--Matérn fields (with FEM approximation)

```{r}
B.tau = cbind(0, log(tau), 0, 0, 0)
B.kappa = cbind(0, 0, log(kappa), 0, 0)
op <- rSPDE::spde.matern.operators(graph = graph_copy2,
                                      B.tau = B.tau,
                                      B.kappa =  B.kappa,
                                      parameterization = "spde",
                                      theta = c(1,1,0,0),
                                      alpha = alpha)
# Compute the covariance matrix
est_cov_matrix <- covariance_mesh(op)
# Compute the standard deviation
est_sigma_s <- sqrt(Matrix::diag(est_cov_matrix))
```

```{r}
B.tau = cbind(0, log(est_sigma_s), 0, 0, 0)
B.kappa = cbind(0, 0, rep(log(kappa), length(log(est_sigma_s))), 0, 0)
op <- rSPDE::spde.matern.operators(graph = graph_copy2,
                                      B.tau = B.tau,
                                      B.kappa =  B.kappa,
                                      parameterization = "spde",
                                      theta = c(1,1,0,0),
                                      alpha = alpha)
# Compute the covariance matrix
est_cov_matrix <- covariance_mesh(op)
# Compute the standard deviation
est_sigma_0 <- sqrt(Matrix::diag(est_cov_matrix))
```


```{r}
msdwmf_fem <- graph_copy2$plot_function(X = est_sigma_s, vertex_size = 1, type = "plotly", line_color = "#0000C8", line_width = gsw, edge_color = "black", edge_width = gsw) %>% 
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("\\sigma_{\\kappa}(\\cdot)"), y = 0.8),
         font = list(family = "Palatino"),
         margin = list(l = 0, r = 0, b = 0, t = 0),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1, y = 1, z = 1),
camera = list(
      eye = list(x = -0.7*a, y = 0.7*a, z = 0.7*a))))


msdvswmf_fem <- graph_copy2$plot_function(X = est_sigma_0, vertex_size = 1, type = "plotly", line_color = "darkgreen", line_width = gsw, edge_color = "black", edge_width = gsw) %>%  
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("\\sigma_0"), y = 0.8),
         font = list(family = "Palatino"),
         margin = list(l = 0, r = 0, b = 0, t = 0),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1, y = 1, z = 1),
camera = list(
      eye = list(x = -0.7*a, y = 0.7*a, z = 0.7*a))))

save(msdwmf_fem, file = here::here("data_files/msdwmf_fem.Rdata"))
save(msdvswmf_fem, file = here::here("data_files/msdvswmf_fem.Rdata"))
```


:::: {style="display: grid; grid-template-columns: 485px 485px 485px; grid-column-gap: 0px;"}


::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Marginal standard deviation $\\sigma_\\kappa(\\cdot)$ of a Whittle--Matérn field with $\\tau = 1$.")}
load(here::here("data_files/msdwmf_fem.Rdata"))
msdwmf_fem
```


:::


::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Marginal standard deviation $\\sigma_0$ of a Generalized Whittle--Matérn field with $\\tau(\\cdot) = \\sigma_\\kappa(\\cdot)$.")}
load(here::here("data_files/msdvswmf_fem.Rdata"))
msdvswmf_fem
```


:::



::::

# References


```{r, eval = TRUE}
grateful::cite_packages(output = "paragraph", out.dir = ".")
```


