---
title: "The rol of $\\tau$"
date: "Last modified: `r format(Sys.time(), '%d-%m-%Y.')`"
output:
  html_document:
    mathjax: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
    highlight: pygments
    theme: flatly
    code_folding: hide # class.source = "fold-hide" to hide code and add a button to show it
    df_print: paged
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
    fig_caption: true
    code_download: true
    css: visual.css
always_allow_html: true
bibliography: 
  - references.bib
  - grateful-refs.bib
header-includes:
  - \newcommand{\ar}{\mathbb{R}}
  - \newcommand{\llav}[1]{\left\{#1\right\}}
  - \newcommand{\pare}[1]{\left(#1\right)}
  - \newcommand{\Ncal}{\mathcal{N}}
  - \newcommand{\Vcal}{\mathcal{V}}
  - \newcommand{\Ecal}{\mathcal{E}}
  - \newcommand{\Wcal}{\mathcal{W}}
  - \newcommand{\almosteverywhere}{\mathrm{a.e.}\;}
---

Go back to the [Contents](about.html) page.

<div style="color: #2c3e50; text-align: right;">
********  
<strong>Press Show to reveal the code chunks.</strong>  

********
</div>


Below we set some global options for all code chunks in this document.


```{r}
# Create a clipboard button on the rendered HTML page
source(here::here("clipboard.R")); clipboard
# Set seed for reproducibility
set.seed(593) 
# Set global options for all code chunks
knitr::opts_chunk$set(
  # Disable messages printed by R code chunks
  message = FALSE,    
  # Disable warnings printed by R code chunks
  warning = FALSE,    
  # Show R code within code chunks in output
  echo = TRUE,        
  # Include both R code and its results in output
  include = TRUE,     
  # Evaluate R code chunks
  eval = FALSE,       
  # Enable caching of R code chunks for faster rendering
  cache = FALSE,      
  # Align figures in the center of the output
  fig.align = "center",
  # Enable retina display for high-resolution figures
  retina = 2,
  # Show errors in the output instead of stopping rendering
  error = TRUE,
  # Do not collapse code and output into a single block
  collapse = FALSE
)
# Start the figure counter
fig_count <- 0
# Define the captioner function
captioner <- function(caption) {
  fig_count <<- fig_count + 1
  paste0("Figure ", fig_count, ": ", caption)
}
# Define the function to truncate a number to two decimal places
truncate_to_two <- function(x) {
  truncated <- floor(x * 100) / 100
  sprintf("%.2f", truncated)
}
```



Below we load the necessary libraries and define the auxiliary functions.

```{r, eval = TRUE}
library(rSPDE)
library(MetricGraph)

library(dplyr)
library(plotly)
library(scales)
library(patchwork)
library(tidyr)

library(here)
library(rmarkdown)
# Cite all loaded packages
library(grateful)

library(slackr)
source("keys.R")
slackr_setup(token = token) # token comes from keys.R
```


```{r}
capture.output(
  knitr::purl(here::here("functionality1.Rmd"), output = here::here("functionality1.R")),
  file = here::here("old/purl_log.txt")
)
source(here::here("functionality1.R"))
```


```{r}
gets_f_in_dist_mesh <- function(graph, f_values){
  VtE <- graph$mesh$VtE
  E <- graph$E
  nE <- graph$nE
  nV <- graph$nV
  E_ext <- data.frame(edge_number = 1:nE, vertex_start = E[,1], vertex_end = E[,2])
  
  original_vertex <- VtE[1:nV,]
  f <- f_values[1:nV]
  
  no_vertices <- cbind(VtE[(nV+1):length(f_values),], f_values[(nV+1):length(f_values)])
  
  same_vertex_list <- list()
  for (i in 1:nE) {
    same_vertex_list[[i]] <- E_ext %>% 
      filter(vertex_start == i | vertex_end == i) %>%
      mutate(lor = case_when(vertex_start == i ~ 0,vertex_end == i ~ 1)) %>% 
      dplyr::select(edge_number, lor) %>% 
      as.matrix()
  }
  
  for (i in seq_len(nrow(original_vertex))) {
    current_row <- original_vertex[i, ]
    # Find which matrix in same_vertex_list contains this row
    for (j in seq_along(same_vertex_list)) {
      if (any(apply(same_vertex_list[[j]], 1, function(x) all(x == current_row)))) {
        # Add a new column with the corresponding value from f
        same_vertex_list[[j]] <- cbind(same_vertex_list[[j]], f[i])
        break
      }
    }
  }
  
  result_matrix <- do.call(rbind, same_vertex_list)
  return(rbind(no_vertices, result_matrix))
}
```


Let's build a small graph to illustrate the effect of $\tau$ on the graph.

```{r}
edge1 <- rbind(c(0,0),c(1,0))
edge2 <- rbind(c(0,0),c(0,1))
edge3 <- rbind(c(0,1),c(-1,1))
theta <- seq(from = pi,to = 3*pi/2,length.out = 50)
edge4 <- cbind(sin(theta),1+ cos(theta))
edges <- list(edge1, edge2, edge3, edge4)
```

```{r}
h = 0.01
graph <- metric_graph$new(edges = edges)
aux_graph <- graph$clone()
graph$build_mesh(h=h, continuous = TRUE)
edge_number <- graph$mesh$VtE
XY_graph <- graph$mesh$V

aux_graph$build_mesh(h=h, continuous = FALSE)
aux_edge_number <- aux_graph$mesh$VtE
aux_XY_graph <- aux_graph$mesh$V
```


Let $f(s) = \mathrm{edge.number}(s)/4$ and $g(s) = 0.5 \cdot (x^2(s) - y^2(s)) + 0.5$, where $(x(s), y(s))$ denote the Euclidean coordinates on the plane (see Figures 1 and 2). Clearly, $f$ is continuous, whereas $g$ is discontinuous. These functions serve as covariates in the analysis.

```{r}
f <- edge_number[,1]/4 # discontinuous covariate
g <- 0.5*(XY_graph[, 1]^2 - XY_graph[, 2]^2) + 0.5 # continuous covariate

aux_f <- aux_edge_number[,1]/4# discontinuous covariate
aux_g <- 0.5*(aux_XY_graph[, 1]^2 - aux_XY_graph[, 2]^2) + 0.5 # continuous covariate
```


```{r}
a = 2
```



# Plot the covariates.


```{r}
cov_f <- aux_graph$plot_function(aux_f, vertex_size = 1, type = "plotly", line_color = "#0000C8", line_width = gsw, continuous = FALSE, interpolate_plot = FALSE, edge_width = gsw) %>%  
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("f(s) = \\mathrm{edge.number}(s)/4"), y = 0.85),
font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

cov_g <- graph$plot_function(g, vertex_size = 1, type = "plotly", line_color = "red", line_width = gsw, edge_width = gsw) %>%  
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("g(s) = 0.5 \\cdot (x^2(s) - y^2(s)) + 0.5"), y = 0.85),
font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

save(cov_f, file = here::here("data_files/cov_f.Rdata"))
save(cov_g, file = here::here("data_files/cov_g.Rdata"))
```

:::: {style="display: grid; grid-template-columns: 485px 485px 485px; grid-column-gap: 0px;"}

::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Discontinuous covariate $f(s) = \\mathrm{edge.number}(s)/4$.")}
load(here::here("data_files/cov_f.Rdata"))
cov_f
```


:::

::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Continuous covariate $g(s) = 0.5 \\cdot (x^2(s) - y^2(s)) + 0.5$.")}
load(here::here("data_files/cov_g.Rdata"))
cov_g
```


:::

::::


```{r}
normal_sample <- rnorm(length(g))
```


# Both covariates are continuous

We now consider the case where both covariates are continuous, that is $\tau(s) = \exp(g(s))$ and $\kappa(s) = \exp(g(s))$. Using these, we simulate $u(s)$. See Figures 3,4, and 5.


```{r}
# Define the matrices B.tau and B.kappa
B.tau =   cbind(0, 1, 0, g, 0)
B.kappa = cbind(0, 0, 1, 0, g)
# Log-regression coefficients
theta <- c(0, 0, 1, 1) 
# Choose alpha
nu = 2.5
alpha = nu + 1/2
# Compute the operator
op <- rSPDE::spde.matern.operators(graph = graph,
                                      B.tau = B.tau,
                                      B.kappa =  B.kappa,
                                      parameterization = "spde",
                                      theta = theta,
                                      alpha = alpha)
# Simulate the non-stationary field
Sigma <- precision(op)
R <- chol(Sigma)
u = solve(R, normal_sample)

model_for_tau <- exp(B.tau[,-1]%*%theta)
model_for_kappa <- exp(B.kappa[,-1]%*%theta)
```


```{r}
kkk1 <- graph$plot_function(model_for_tau, vertex_size = 1, type = "plotly", line_color = "#0000C8", line_width = gsw, edge_width = gsw) %>%  
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("\\tau(s) = \\exp(g(s))"), y = 0.85),
font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

kkk2 <- graph$plot_function(model_for_kappa, vertex_size = 1, type = "plotly", line_color = "red", line_width = gsw, edge_width = gsw) %>%  
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("\\kappa(s) = \\exp(g(s))"), y = 0.85),
font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

kkk3 <- graph$plot_function(X = u, vertex_size = 1, type = "plotly", line_color = "darkgreen", line_width = gsw, edge_width = gsw) %>%  
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("u(s)"), y = 0.85),
font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))


save(kkk1, file = here::here("data_files/kkk1.Rdata"))
save(kkk2, file = here::here("data_files/kkk2.Rdata"))
save(kkk3, file = here::here("data_files/kkk3.Rdata"))
```


:::: {style="display: grid; grid-template-columns: 485px 485px 485px; grid-column-gap: 0px;"}

::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Model for $\\tau(s)$.")}
load(here::here("data_files/kkk1.Rdata"))
kkk1
```

:::

::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Model for $\\kappa(s)$.")}
load(here::here("data_files/kkk2.Rdata"))
kkk2
```


:::

::: {}


```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Simulated field $u(s)$.")}
load(here::here("data_files/kkk3.Rdata"))
kkk3
```

:::

::::


# Both covariates are discontinuos

We now consider the case where both covariates are discontinuous, that is $\tau(s) = \exp(f(s))$ and $\kappa(s) = \exp(f(s))$. Using these, we simulate $u(s)$. See Figures 6,7, and 8.

```{r}
tau <- 1
# Define the matrices B.tau and B.kappa
B.tau <- cbind(0, 1, 0, log(tau)*rep(1, length(f)), 0)
realB.tau <- cbind(0, 1, 0, f, 0)
B.kappa = cbind(0, 0, 1, 0, f)
# Log-regression coefficients
theta <- c(0, 0, 1, 1) 
# Compute the operator
op1 <- rSPDE::spde.matern.operators(graph = graph,
                                      B.tau = B.tau,
                                      B.kappa =  B.kappa,
                                      parameterization = "spde",
                                      theta = theta,
                                      alpha = alpha)

realmodel_for_tau <- exp(realB.tau[,-1]%*%theta)
normal_sample1 <- normal_sample #rnorm(length(g))

Sigma1 <- precision(op1)
R1 <- chol(Sigma1)
u1cont <- solve(R1, normal_sample1)
u1 <-u1cont*tau/realmodel_for_tau

op2 <- rSPDE::spde.matern.operators(graph = graph,
                                      B.tau = realB.tau,
                                      B.kappa =  B.kappa,
                                      parameterization = "spde",
                                      theta = theta,
                                      alpha = alpha)
Sigma2 <- precision(op2)
R2 <- chol(Sigma2)
u2 = solve(R2, normal_sample1)

# To plot the models for tau and kappa
aux_B.tau =   cbind(0, 1, 0, aux_f, 0)
aux_B.kappa = cbind(0, 0, 1, 0, aux_f)
model_for_tau <- exp(aux_B.tau[,-1]%*%theta)
model_for_kappa <- exp(aux_B.kappa[,-1]%*%theta)
```




```{r}
gg <- gets_f_in_dist_mesh(graph, u1cont)
aux_df <- data.frame(.edge_number = gg[,1], .distance_on_edge = gg[,2], f = gg[,3])
another_df <- cbind(tau/model_for_tau, aux_graph$mesh$VtE)
colnames(another_df) <- c("tau_rel", ".edge_number", ".distance_on_edge")
another_df <- as.data.frame(another_df)
# Step 1: Sort aux_df by the four columns
aux_df_sorted <- aux_df %>%
  arrange(.edge_number, .distance_on_edge)

another_df_sorted <- another_df %>%
  arrange(.edge_number, .distance_on_edge)
# Merge
merged_df <- cbind(aux_df_sorted, another_df_sorted)[c(1:4)] %>% mutate(final_f = f*tau_rel) %>% dplyr::select(-tau_rel, -f) %>% rename(edge_number = .edge_number, distance_on_edge = .distance_on_edge, f = final_f)

prod <- aux_graph$process_data(data = merged_df, normalized = TRUE)
```


```{r}
kkk4 <- aux_graph$plot_function(model_for_tau, vertex_size = 1, type = "plotly", line_color = "#0000C8", line_width = gsw, edge_width = gsw) %>%  
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("\\tau(s) = \\exp(f(s))"), y = 0.85),
font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

kkk5 <- aux_graph$plot_function(model_for_kappa, vertex_size = 1, type = "plotly", line_color = "red", line_width = gsw, edge_width = gsw) %>%  
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("\\kappa(s) = \\exp(f(s))"), y = 0.85),
font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

kkk6 <- aux_graph$plot_function(data = "f", newdata= prod, vertex_size = 1, type = "plotly", line_color = "darkgreen", line_width = gsw, continuous = FALSE, edge_width = gsw) %>%  
  config(mathjax = 'cdn') %>% 
  layout(title = list(text = TeX("u(s)"), y = 0.85),
font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))


save(kkk4, file = here::here("data_files/kkk4.Rdata"))
save(kkk5, file = here::here("data_files/kkk5.Rdata"))
save(kkk6, file = here::here("data_files/kkk6.Rdata"))
```


:::: {style="display: grid; grid-template-columns: 485px 485px 485px; grid-column-gap: 0px;"}

::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Model for $\\tau(s)$.")}
load(here::here("data_files/kkk4.Rdata"))
kkk4
```

:::

::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Model for $\\kappa(s)$.")}
load(here::here("data_files/kkk5.Rdata"))
kkk5
```


:::

::: {}


```{r, eval =TRUE, fig.height = 7, out.width = "100%", fig.cap = captioner("Simulated field $u(s)$.")}
load(here::here("data_files/kkk6.Rdata"))
kkk6
```

:::

::::




# The covariate for $\tau$ is discontinuous and the covariate for $\kappa$ is continuous

We now consider the case where the covariate for $\tau$ is discontinuous and the covariate for $\kappa$ is continuous, that is $\tau(s) = \exp(f(s))$ and $\kappa(s) = \exp(g(s))$. Using these, we simulate $u(s)$. See Figures 12, 13, and 14.

```{r}
# Define the matrices B.tau and B.kappa
B.tau <- cbind(0, 1, 0, log(tau)*rep(1, length(f)), 0)
realB.tau <- cbind(0, 1, 0, f, 0)
B.kappa = cbind(0, 0, 1, 0, g)
# Log-regression coefficients
theta <- c(0, 0, 1, 1)
# Compute the operator
op1 <- rSPDE::spde.matern.operators(graph = graph,
                                      B.tau = B.tau,
                                      B.kappa =  B.kappa,
                                      parameterization = "spde",
                                      theta = theta,
                                      alpha = alpha)

realmodel_for_tau <- exp(realB.tau[,-1]%*%theta)
normal_sample2 <- normal_sample#rnorm(length(g))

Sigma1 <- precision(op1)
R1 <- chol(Sigma1)
u1cont <- solve(R1, normal_sample2)
u1 <-u1cont*tau/realmodel_for_tau

op2 <- rSPDE::spde.matern.operators(graph = graph,
                                    B.tau = realB.tau,
                                    B.kappa =  B.kappa,
                                    parameterization = "spde",
                                    theta = theta,
                                    alpha = alpha)
Sigma2 <- precision(op2)
R2 <- chol(Sigma2)
u2 = solve(R2, normal_sample2)

# To plot the models for tau and kappa
aux_B.tau =   cbind(0, 1, 0, aux_f, 0)
model_for_tau <- exp(aux_B.tau[,-1]%*%theta)
model_for_kappa <- exp(B.kappa[,-1]%*%theta)
```

```{r}
gg <- gets_f_in_dist_mesh(graph, u1cont)
aux_df <- data.frame(.edge_number = gg[,1], .distance_on_edge = gg[,2], f = gg[,3])
another_df <- cbind(tau/model_for_tau, aux_graph$mesh$VtE)
colnames(another_df) <- c("tau_rel", ".edge_number", ".distance_on_edge")
another_df <- as.data.frame(another_df)
# Step 1: Sort aux_df by the four columns
aux_df_sorted <- aux_df %>%
  arrange(.edge_number, .distance_on_edge)

another_df_sorted <- another_df %>%
  arrange(.edge_number, .distance_on_edge)
# Merge
merged_df <- cbind(aux_df_sorted, another_df_sorted)[c(1:4)] %>% mutate(final_f = f*tau_rel) %>% dplyr::select(-tau_rel, -f) %>% rename(edge_number = .edge_number, distance_on_edge = .distance_on_edge, f = final_f)

prod <- aux_graph$process_data(data = merged_df, normalized = TRUE)
```


```{r}
kkk7 <- aux_graph$plot_function(model_for_tau, vertex_size = 1, type = "plotly", line_color = "#0000C8", line_width = gsw, edge_color = "black", edge_width = gsw) %>%
  config(mathjax = 'cdn') %>%
  layout(font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

kkk8 <- graph$plot_function(model_for_kappa, vertex_size = 1, type = "plotly", line_color = "red", line_width = gsw, edge_color = "black", edge_width = gsw) %>%
  config(mathjax = 'cdn') %>%
  layout(font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

kkk9 <- aux_graph$plot_function(data = "f", newdata= prod, vertex_size = 1, type = "plotly", line_color = "darkgreen", line_width = gsw, continuous = FALSE, interpolate_plot = FALSE, edge_color = "black", edge_width = gsw) %>%
  config(mathjax = 'cdn') %>%
  layout(font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

save(kkk7, file = here::here("data_files/kkk7.Rdata"))
save(kkk8, file = here::here("data_files/kkk8.Rdata"))
save(kkk9, file = here::here("data_files/kkk9.Rdata"))
```



# The covariate for $\tau$ is continuous and the covariate for $\kappa$ is discontinuous

We now consider the case where the covariate for $\tau$ is continuous and the covariate for $\kappa$ is discontinuous, that is $\tau(s) = \exp(g(s))$ and $\kappa(s) = \exp(f(s))$. Using these, we simulate $u(s)$. See Figures 9, 10, and 11.

```{r}
# Define the matrices B.tau and B.kappa
B.tau =   cbind(0, 1, 0, g, 0) #rep(1, length(f))
B.kappa = cbind(0, 0, 1, 0, f)
# Log-regression coefficients
theta <- c(0, 0, 1, 1)
# Compute the operator
op <- rSPDE::spde.matern.operators(graph = graph,
                                      B.tau = B.tau,
                                      B.kappa =  B.kappa,
                                      parameterization = "spde",
                                      theta = theta,
                                      alpha = alpha)
# Simulate the non-stationary field
Sigma <- precision(op)
R <- chol(Sigma)
u = solve(R, normal_sample)

aux_B.kappa = cbind(0, 0, 1, 0, aux_f)
model_for_tau <- exp(B.tau[,-1]%*%theta)
model_for_kappa <- exp(aux_B.kappa[,-1]%*%theta)
```


```{r}
kkk10 <- graph$plot_function(model_for_tau, vertex_size = 1, type = "plotly", line_color = "#0000C8", line_width = gsw, edge_color = "black", edge_width = gsw) %>%
  config(mathjax = 'cdn') %>%
  layout(font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

kkk11 <- aux_graph$plot_function(model_for_kappa, vertex_size = 1, type = "plotly", line_color = "red", line_width = gsw, edge_color = "black", edge_width = gsw) %>%
  config(mathjax = 'cdn') %>%
  layout(font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

kkk12 <- graph$plot_function(X = u, vertex_size = 1, type = "plotly", line_color = "darkgreen", line_width = gsw, edge_color = "black", edge_width = gsw) %>%
  config(mathjax = 'cdn') %>%
  layout(font = list(family = "Palatino"),
         showlegend = FALSE,
         scene = list(xaxis = list(title = list(text = "x", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              yaxis = list(title = list(text = "y", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
              zaxis = list(title = list(text = "z", font = list(color = colaxnn)),  tickfont = list(color = colaxnn)),
           aspectratio = list(x = 1/2, y = 1, z = 1),
camera = list(
      eye = list(x = -1*a, y = 0.5*a, z = 0.7*a))))

save(kkk10, file = here::here("data_files/kkk10.Rdata"))
save(kkk11, file = here::here("data_files/kkk11.Rdata"))
save(kkk12, file = here::here("data_files/kkk12.Rdata"))
```



:::: {style="display: grid; grid-template-columns: 485px 485px 485px; grid-column-gap: 0px;"}

::: {}

```{r, echo = FALSE, eval =TRUE, fig.height = 7, out.width = "100%"}
load(here::here("data_files/kkk10.Rdata"))
kkk10
```

:::

::: {}

```{r, echo = FALSE, eval =TRUE, fig.height = 7, out.width = "100%"}
load(here::here("data_files/kkk11.Rdata"))
kkk11
```


:::

::: {}


```{r, echo = FALSE, eval =TRUE, fig.height = 7, out.width = "100%"}
load(here::here("data_files/kkk12.Rdata"))
kkk12
```

:::

::::



:::: {style="display: grid; grid-template-columns: 485px 485px 485px; grid-column-gap: 0px;"}

::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%"}
load(here::here("data_files/kkk7.Rdata"))
kkk7
```

:::

::: {}

```{r, eval =TRUE, fig.height = 7, out.width = "100%"}
load(here::here("data_files/kkk8.Rdata"))
kkk8
```


:::

::: {}


```{r, eval =TRUE, fig.height = 7, out.width = "100%"}
load(here::here("data_files/kkk9.Rdata"))
kkk9
```

:::

::::


# References


```{r, eval = TRUE}
grateful::cite_packages(output = "paragraph", out.dir = ".")
```


